---
title: "Pupillometry and Reaction Time"
author: "Jeremy Elman"
date: "`r Sys.Date()`"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

Load libraries
```{r results='hide', message=FALSE, warning=FALSE}
library(ggplot2)
library(gridExtra)
library(gtools)
library(lme4)
library(arm)
library(lmerTest)
library(dplyr)
library(magrittr)
library(sjPlot)
library(sjmisc)
library(multcomp)
source("~/netshare/K/code/misc/summarySE.R")
source("~/netshare/K/code/misc/normDataWithin.R")
source("~/netshare/K/code/misc/summarySEwithin.R")
source("~/netshare/K/code/misc/get_legend.R")
```

Load data.
```{r}
pupilRT = read.csv("~/netshare/K/Projects/Pupil_ReactionTime/data/pupil_RT.csv", 
                         stringsAsFactors = FALSE)
pupilRT = pupilRT[!is.na(pupilRT$PCA) & !is.na(pupilRT$rMCI_cons_v2pe),]
pupilRT = subset(pupilRT, (VETSAGRP=='V1V2') | (VETSAGRP=='V2AR'))
str(pupilRT)
```

Recode two-level factors to 0/1. Center continuous data.
*TRANSFORM*
```{r}
# Create factors
pupilRT$facLoad = factor(pupilRT$Load)
pupilRT$facLoad = relevel(pupilRT$facLoad, ref="6")
pupilRT$MZ = ifelse(pupilRT$zygos==1, 1, 0)
pupilRT$site_v2rev = ifelse(pupilRT$site_v2rev==1, 1, 0)
pupilRT$Device = factor(pupilRT$LR_Device)
pupilRT$acamedbin = ifelse(pupilRT$acamedtot==0, 0, 1)

#Bin MCI data into 0 = No impairment, 1 = Single domain MCI, 2 = Multi-domain MCI.
pupilRT$rMCI_cons_3grp = ifelse(pupilRT$rMCI_cons_v2pe==0, 0, 
                                        ifelse(pupilRT$rMCI_cons_v2pe==1 | 
                                               pupilRT$rMCI_cons_v2pe==2, 1, 2))
pupilRT$rMCI_cons_3grp = factor(pupilRT$rMCI_cons_3grp, 
                                   labels=c("CN","SMCI","MMCI"))

#Bin MCI data into 0 = No impairment, 1 = Non-amnestic S-MCI, 2 = Amnestic S-MCI, 3 = Multi-domain MCI.
pupilRT$rMCI_cons_4grp = pupilRT$rMCI_cons_v2pe
pupilRT$rMCI_cons_4grp = gsub(4, 3, pupilRT$rMCI_cons_4grp)
pupilRT$rMCI_cons_4grp = factor(pupilRT$rMCI_cons_4grp,
                                   labels=c("CN","naSMCI","aSMCI","MMCI"))

# Original MCI categories: 0 = No impairment, 1 = Non-amnestic S-MCI, 2 = Amnestic S-MCI, 3 = Non-amnestic M-MCI, 4 = Amnestic M-MCI
pupilRT$rMCI_cons_v2pe = factor(pupilRT$rMCI_cons_v2pe, 
                                   labels=c("CN","naSMCI","aSMCI","naMMCI","aMMCI"))

# Center continuous variables to interpret intercept at mean value (rather than 0).
# Subject specific variables centered at subject level, trial specific variables centered at trial level.

# Trial specific variables
contTrialVars = c("PCA","pctPCA","adjPCA")

# Center trial specific variables
for (x in contTrialVars) {
  newcol = paste0('c.',x)
  pupilRT[[newcol]] = as.numeric(scale(pupilRT[[x]], center=TRUE, scale=FALSE))
}

# Subject specific variables centered at subject level.
contSubjVars = c("age_v2","nas201tran","DSFMAX_V2_nasp")

# Center subject specific variables
subjDF = pupilRT[c("vetsaid",contSubjVars)]
subjDF %<>% group_by(vetsaid) %>% dplyr::summarise_each(funs(mean))
nums <- sapply(subjDF, is.numeric)
c.subjDF = as.data.frame(apply(subjDF[,nums],2, function(y) y - mean(y, na.rm=TRUE)))
names(c.subjDF) = paste0("c.",names(c.subjDF))
c.subjDF$vetsaid = subjDF$vetsaid
pupilRT = left_join(pupilRT, c.subjDF, by="vetsaid")


### Generate new subject level variables ###

# Create subject level dataset of RT variables
subjRT = pupilRT %>%
  select(vetsaid, ends_with("LOG_V2_nasp")) %>%
  group_by(vetsaid) %>%
  summarise_all(funs(first))

# Derive RT metrics such as CV and residSTD
# Coefficient of Variation = STD / MEAN
subjRT = subjRT %>% 
  mutate(SRTLCV_V2_nasp = SRTLSTDLOG_V2_nasp/SRTLMEANLOG_V2_nasp,
         SRTRCV_V2_nasp = SRTRSTDLOG_V2_nasp/SRTRMEANLOG_V2_nasp,
         SRTGCV_V2_nasp = SRTGSTDLOG_V2_nasp/SRTGMEANLOG_V2_nasp,
         CHRTLCV_V2_nasp = CHRTLSTDLOG_V2_nasp/CHRTLMEANLOG_V2_nasp,
         CHRTRCV_V2_nasp = CHRTRSTDLOG_V2_nasp/CHRTRMEANLOG_V2_nasp,
         CHRTGCV_V2_nasp = CHRTGSTDLOG_V2_nasp/CHRTGMEANLOG_V2_nasp)

# Standard deviation orthogonalized with respect to mean
subjRT$residSRTLSTDLOG_V2_nasp = resid(lm(SRTLSTDLOG_V2_nasp ~ SRTLMEANLOG_V2_nasp, data=subjRT, na.action="na.exclude"))
subjRT$residSRTRSTDLOG_V2_nasp = resid(lm(SRTRSTDLOG_V2_nasp ~ SRTRMEANLOG_V2_nasp, data=subjRT, na.action="na.exclude"))
subjRT$residSRTGSTDLOG_V2_nasp = resid(lm(SRTGSTDLOG_V2_nasp ~ SRTGMEANLOG_V2_nasp, data=subjRT, na.action="na.exclude"))
subjRT$residCHRTLSTDLOG_V2_nasp = resid(lm(CHRTLSTDLOG_V2_nasp ~ CHRTLMEANLOG_V2_nasp, data=subjRT, na.action="na.exclude"))
subjRT$residCHRTRSTDLOG_V2_nasp = resid(lm(CHRTRSTDLOG_V2_nasp ~ CHRTRMEANLOG_V2_nasp, data=subjRT, na.action="na.exclude"))
subjRT$residCHRTGSTDLOG_V2_nasp = resid(lm(CHRTGSTDLOG_V2_nasp ~ CHRTGMEANLOG_V2_nasp, data=subjRT, na.action="na.exclude"))

# Merge back into full pupil dataset
pupilRT = pupilRT %>%
    left_join(subjRT, by="vetsaid") %>% 
    dplyr::select(-ends_with(".x"))

names(pupilRT) = gsub(".y","",names(pupilRT), fixed=T)


# Create quantile groups
qVars = names(pupilRT)[grepl("_V2_nasp", names(pupilRT)) & !grepl("c.", names(pupilRT))]
new.qVars = qVars
names(new.qVars) = paste0("q.",qVars)
pupilRT = pupilRT %>%
  group_by(vetsaid) %>%
  dplyr::summarise_each_(funs(first),qVars) %>%
  mutate_each_(funs(quantcut(., labels=seq(1,4))),qVars) %>%
  dplyr::select_("vetsaid"="vetsaid",.dots=new.qVars) %>%
  inner_join(pupilRT, by="vetsaid")

qVars = names(pupilRT)[grepl("_V2_nasp", names(pupilRT)) & !grepl("c.", names(pupilRT))]
new.qVars = qVars
names(new.qVars) = paste0("q.",qVars)

quantDF = pupilRT %>%
  group_by(vetsaid) %>%
  summarise_at(vars(one_of(qVars)), funs(first)) %>%
  mutate_at(vars(one_of(qVars)), funs(quantcut), labels=seq(1,4)) %>%
  dplyr::select_("vetsaid"="vetsaid",.dots=new.qVars) 
 
pupilRT = pupilRT %>%
  inner_join(quantDF, by="vetsaid")

# Create residPCA by regressing BaselineDiameter from PCA and taking the residuals.
lme.PCA.resid = lmer(PCA ~ BaselineDiameter + (1 | case/vetsaid),
                     data=pupilRT)
pupilRT$residPCA = resid(lme.PCA.resid)
```

# Basic sample descriptives
```{r, include=FALSE}
#Create dataset with subject level variables to assess relationships with BOLD variance.
subjDatRT = pupilRT %>% 
            dplyr::select(-contains("PCA"),-contains("Load")) %>%
            group_by(vetsaid) %>%
            summarise_all(funs(first))
```

How many subjects?
```{r}
n_distinct(subjDatRT$vetsaid)
```

How many attrition replacements?
```{r}
dplyr::count(subjDatRT, VETSAGRP)
```

How many twin pairs vs unpaired twins? 
```{r}
subjDatRT %>%
  group_by(case) %>%
  dplyr::summarise(n_twins = n_distinct(vetsaid)) %>%
  dplyr::count(n_twins)
```


How many MZ and DZ pairs? (excludes unpaired subjects)
```{r}
subjDatRT %>% 
  group_by(case) %>%
  mutate(n_twins = n_distinct(vetsaid)) %>%
  filter(n_twins > 1) %>%
  dplyr::summarise(zyg = mean(zygos)) %>%
  group_by(zyg) %>%
  dplyr::count(zyg)
```

How many levels of load did subjects complete? Shows number of subjects who completed 1, 2, or 3 levels (corresponding to digit spans of 3, 6, and 9).
```{r}
pupilRT %>%
  group_by(vetsaid) %>%
  dplyr::summarise(load = n()) %>%
  dplyr::count(load)
```

How many of each MCI group?
```{r}
dplyr::count(subjDatRT, rMCI_cons_v2pe)
```

How many of each MCI group binned by single or multi-doman MCI?
```{r}
dplyr::count(subjDatRT, rMCI_cons_3grp)
```

How many of each MCI group binned by single amnestic/non-amnestic or multi-doman MCI?
```{r}
dplyr::count(subjDatRT, rMCI_cons_4grp)
```

Plot frequencies of MCI measures
```{r}
sjp.frq(subjDatRT$rMCI_cons_4grp, 
          title="MCI groups",
          axis.labels=c("Normal","Single Domain\nNon-amnestic",
                         "Single Domain\nAmnestic","Multi Domain"))
```


```{r, include=FALSE}
# pdf("~/netshare/K/Projects/Pupil_ReactionTime/results/RT_MCI_groups.pdf", width=8, height=6)
# grid.arrange(mci.p1$plot,mci.p2$plot)
# dev.off()
```

Plot pctPCA and residPCA data to check for ceiling effects on pupil dilation
```{r}
pctPcaPlot = ggplot(pupilRT, aes(x=pctPCA)) + 
  geom_histogram(fill="steelblue3",color="black",size=.4) + 
  facet_wrap(~ Load, nrow=3) + 
  ggtitle("Histogram of pctPCA by Load") + 
  xlab("% PCA") + theme_bw() 

residPcaPlot = ggplot(pupilRT, aes(x=residPCA)) + 
  geom_histogram(fill="steelblue3",color="black",size=.4) + 
  facet_wrap(~ Load, nrow=3) + 
  ggtitle("Histogram of residPCA by Load") + 
  xlab("PCA (adjusted for baseline)") + theme_bw() 

grid.arrange(pctPcaPlot, residPcaPlot, ncol=2)
```


```{r, include=FALSE}
# pdf("~/netshare/K/Projects/Pupil_ReactionTime/results/Choice_PCAxLoad.pdf")
# grid.arrange(pctPcaPlot, residPcaPlot, ncol=2)
# dev.off()
```

Plot histograms of RT measures
```{r}
rtSubset = pupilRT %>%
  filter(Load==3) %>%
  dplyr::select(contains("CHRTG"), contains("SRTG"), -starts_with("q."))

plot_list = list()
for (i in 1:ncol(rtSubset)) {
  p = ggplot(rtSubset,aes_string(x = rtSubset[[i]])) +
        geom_histogram(fill="steelblue3",color="black",size=.4) + 
        xlab(names(rtSubset[i])) + theme_bw()
  plot_list[[i]] = p
}


do.call(grid.arrange, c(plot_list, list(nrow=4)))
```

```{r, include=FALSE}
# pdf("~/netshare/K/Projects/Pupil_ReactionTime/results/Choice_rtHists.pdf")
# do.call(grid.arrange, c(plot_list, list(ncol=2)))
# dev.off()
```


-------------------------------

# Mixed Effects Models: All MCI groups

Run model testing interaction of load with log mean choice RT
```{r}

lme.facLoad.CHRTGMEANLOG.MCI = lmer(residPCA ~ facLoad*(CHRTGMEANLOG_V2_nasp + 
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + Device + acamedbin + 
                                    (1 | case/vetsaid), data=pupilRT)
summary(lme.facLoad.CHRTGMEANLOG.MCI)
anova(lme.facLoad.CHRTGMEANLOG.MCI)
```

Plot pupil dilation by log mean choice RT quantile
```{r, echo=FALSE}
# Plot raw values
summaryResidPCA.log_meanRT = summarySEwithin(pupilAXCPT, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load",
                betweenvars="q.CPTDPRIME_V2_nasp",
                na.rm=TRUE)
p.Draw = ggplot(summaryResidPCA.dprime, aes(x=Load,y=residPCA,
                                        color=q.CPTDPRIME_V2_nasp,
                                        group=q.CPTDPRIME_V2_nasp)) +
  geom_line(size=1) +
  geom_errorbar(width=.2,size=1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
  theme_bw(20) + ylab("Change in Pupil Diameter") +
  scale_color_brewer(name=" d' quartile", palette='RdBu') + 
          theme(plot.title = element_text(size=20),
                axis.title = element_text(size=18),
                axis.text.x = element_text(size=16),
                legend.background = element_rect(fill = "transparent"),
                legend.justification=c(1,0), legend.position=c(1,0), 
                legend.text.align=1,
                legend.title.align=0,
                legend.title = element_text(size=16),
                legend.text = element_text(size=16))

# Plot predicted values
dfDpred = sjp.int(lme.facLoad.dprime.MCI, type="eff", int.term="facLoad:CPTDPRIME_V2_nasp", 
               swap.pred=T, mdrt.values = "quart", print.plot=F)$data.list[[1]]
levels(dfDpred$grp) = seq(length(levels(dfDpred$grp)))
p.Dpred = ggplot(data=subset(dfDpred, !grp==3), aes(x=x, y=y, color=grp, group=grp)) + 
          geom_line(size=1) +
          geom_errorbar(width=.2,size=1, aes(ymin=conf.low,ymax=conf.high)) +
          ylab(expression(paste("Predicted ", Delta, " Pupil Diameter"))) + xlab("Load") +
          scale_color_brewer(name="d' quartile",palette='RdBu',direction=-1,labels=seq(4)) + 
          scale_x_continuous(breaks=c(3,6,9)) + theme_bw(16) +
          theme(plot.title = element_text(size=20),
                axis.title = element_text(size=18),
                axis.text.x = element_text(size=16),
                legend.background = element_rect(fill = "transparent"),
                legend.justification=c(1,0), legend.position=c(1,0), 
                legend.text.align=1,
                legend.title.align=0,
                legend.title = element_text(size=16),
                legend.text = element_text(size=16))

gDprime = arrangeGrob(p.Draw, p.Dpred,ncol=2)

ggsave("~/netshare/K/Projects/Pupil_AX-CPT/results/pupil_dprime_All.png", gDprime, height=6, width=12, dpi=300)
```

Test for differences based on mean RT within each level of Load
```{r}
lme.log_meanRT.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ log_meanRT + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_V2_nasp + 
                    rMCI_cons_4grp + c.nas201tran + 
                    (1 | case), 
         data=filter(pupilRT, Load==x))
})
lapply(lme.log_meanRT.loads.MCI, summary)
```

Run model testing interaction of Load with log median RT, digit span and MCI
```{r}
contrasts.facLoad.log_medianRT.MCI = rbind(
    'Load3:log_medianRT vs Load6:log_medianRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,0,0,0),
    'Load6:log_medianRT vs Load9:log_medianRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
    'Load3:log_medianRT vs Load9:log_medianRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0)
)

lme.facLoad.log_medianRT.MCI = lmer(residPCA ~ facLoad*(log_medianRT + 
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + 
                                    Device + acamedbin + c.nas201tran + 
                                    (1 | case/vetsaid), data=pupilRT)
summary(lme.facLoad.log_medianRT.MCI)
summary(glht(lme.facLoad.log_medianRT.MCI, 
             contrasts.facLoad.log_medianRT.MCI),
             test = adjusted("none"))
```

Test for differences based on median RT within each level of Load
```{r}
lme.log_medianRT.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ log_medianRT + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_V2_nasp + 
                    rMCI_cons_4grp + c.nas201tran + 
                    (1 | case), 
         data=filter(pupilRT, Load==x))
})
lapply(lme.log_medianRT.loads.MCI, summary)
```

Run model testing interaction of Load with log std RT, digit span and MCI
```{r}
contrasts.facLoad.log_stdRT.MCI = rbind(
    'Load3:log_stdRT vs Load6:log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,0,0,0),
    'Load6:log_stdRT vs Load9:log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
    'Load3:log_stdRT vs Load9:log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0)
)

lme.facLoad.log_stdRT.MCI = lmer(residPCA ~ facLoad*(log_stdRT + 
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + 
                                    Device + acamedbin + c.nas201tran + 
                                    (1 | case/vetsaid), data=pupilRT)
summary(lme.facLoad.log_stdRT.MCI)
summary(glht(lme.facLoad.log_stdRT.MCI, 
             contrasts.facLoad.log_stdRT.MCI),
             test = adjusted("none"))
```

Test for differences based on std RT within each level of Load
```{r}
lme.log_stdRT.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ log_stdRT + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_V2_nasp + 
                    rMCI_cons_4grp + c.nas201tran + 
                    (1 | case), 
         data=filter(pupilRT, Load==x))
})
lapply(lme.log_stdRT.loads.MCI, summary)
```

Run model testing interaction of Load with log cv RT, digit span and MCI
```{r}
contrasts.facLoad.log_cvRT.MCI = rbind(
    'Load3:log_cvRT vs Load6:log_cvRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,0,0,0),
    'Load6:log_cvRT vs Load9:log_cvRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
    'Load3:log_cvRT vs Load9:log_cvRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0)
)

lme.facLoad.log_cvRT.MCI = lmer(residPCA ~ facLoad*(log_cvRT + 
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + 
                                    Device + acamedbin + c.nas201tran + 
                                    (1 | case/vetsaid), data=pupilRT)
summary(lme.facLoad.log_cvRT.MCI)
summary(glht(lme.facLoad.log_cvRT.MCI, 
             contrasts.facLoad.log_cvRT.MCI),
             test = adjusted("none"))
```

Test for differences based on cv RT within each level of Load
```{r}
lme.log_cvRT.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ log_cvRT + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_V2_nasp + 
                    rMCI_cons_4grp + c.nas201tran + 
                    (1 | case), 
         data=filter(pupilRT, Load==x))
})
lapply(lme.log_cvRT.loads.MCI, summary)
```

----------------------------
# Covariate Plots 

Plot pupil dilation by digit span max quantile
```{r, echo=FALSE}
summaryResidPCA.DSFMAX_V2_nasp = summarySEwithin(pupilRT, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load",
                betweenvars="q.c.DSFMAX_V2_nasp",
                na.rm=TRUE)
  
p.DSFMAX_V2_nasp = summaryResidPCA.DSFMAX_V2_nasp %>%
          filter(q.c.DSFMAX_V2_nasp==1 | q.c.DSFMAX_V2_nasp==4) %>%
          ggplot(., aes(x=Load,y=residPCA,
                        color=q.c.DSFMAX_V2_nasp,
                        group=q.c.DSFMAX_V2_nasp)) +
            geom_line() +
            geom_errorbar(width=.1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
            ggtitle("Max digit span") + theme_bw(16) +
            ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
            scale_color_discrete(name="Max digit span\nquantile",
                                 labels=c("Lower","Upper"))
print(p.DSFMAX_V2_nasp)
ggsave("~/netshare/K/Projects/Pupil_ReactionTime/results/pupilRT_MaxDigitSpan.pdf", p.DSFMAX_V2_nasp)
```

Plot pupil dilation by digit span max quantile
```{r, echo=FALSE}
summaryResidPCA.MCI = summarySEwithin(pupilRT, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load",
                betweenvars="rMCI_cons_4grp",
                na.rm=TRUE)
  
p.MCI = summaryResidPCA.MCI %>%
          ggplot(., aes(x=Load,y=residPCA,
                        color=rMCI_cons_4grp,
                        group=rMCI_cons_4grp)) +
            geom_line() +
            geom_errorbar(width=.1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
            ggtitle("MCI Status") + theme_bw(16) +
            ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
            scale_color_discrete(name="MCI Group", 
                                 labels=c("No MCI",
                                          "Single Domain MCI",
                                          "Multi-Domain MCI"))
print(p.MCI)
ggsave("~/netshare/K/Projects/Pupil_ReactionTime/results/pupilRT_MCI.pdf", p.MCI)
```
----------------------------

```{r, include=FALSE}
#Save out analysis dataset
write.csv(pupilRT,
          "~/netshare/K/Projects/Pupil_ReactionTime/data/pupilDS_ChoiceRT_AnalysisDataset.csv",
          row.names=F)
```

```{r}
print(sessionInfo(), locale = FALSE)
```