---
title: "Pupillometry and Choice Reaction Time"
author: "Jeremy Elman"
date: "`r Sys.Date()`"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

Load libraries
```{r results='hide', message=FALSE, warning=FALSE}
library(ggplot2)
library(gridExtra)
library(gtools)
library(lme4)
library(arm)
library(lmerTest)
library(dplyr)
library(magrittr)
library(sjPlot)
library(sjmisc)
library(multcomp)
source("K:/code/summarySE.R")
source("K:/code/normDataWithin.R")
source("K:/code/summarySEwithin.R")
```

Load data.
```{r}
pupilChoiceRT = read.csv("K:/ReactionTime/data/pupil_choiceRT.csv", 
                         stringsAsFactors = FALSE)
pupilChoiceRT = pupilChoiceRT[!is.na(pupilChoiceRT$PCA) &
                              !is.na(pupilChoiceRT$meanRT),]
str(pupilChoiceRT)
```

How many subjects?
```{r}
n_distinct(pupilChoiceRT$vetsaid)
```

How many attrition replacements?
```{r}
pupilChoiceRT %>% 
  group_by(vetsaid) %>% 
  dplyr::summarise(AR = first(vetsa2)) %>%
  group_by(AR) %>%
  dplyr::summarise(n=n())
```

How many twin pairs vs unpaired twins? 
```{r}
pupilChoiceRT %>%
  group_by(case) %>%
  dplyr::summarise(n_twins = n_distinct(vetsaid)) %>%
  group_by(n_twins) %>%
  dplyr::summarise(n=n())
```


How many MZ and DZ pairs? (excludes unpaired subjects)
```{r}
pupilChoiceRT %>% 
  group_by(case) %>%
  mutate(n_twins = n_distinct(vetsaid)) %>%
  filter(n_twins > 1) %>%
  dplyr::summarise(zyg = mean(zyg14)) %>%
  group_by(zyg) %>%
  dplyr::count(zyg)
```

How many levels of load did subjects complete? Shows number of subjects who completed 1, 2, or 3 levels (corresponding to digit spans of 3, 6, and 9).
```{r}
pupilChoiceRT %>%
  group_by(vetsaid) %>%
  dplyr::summarise(load = n()) %>%
  dplyr::count(load)
```

Recode two-level factors to 0/1. Center continuous data.
*TRANSFORM*
```{r}
# Create factors
pupilChoiceRT$facLoad = factor(pupilChoiceRT$Load)
contr.backward.diff = matrix(c(-2/3, 1/3, 1/3,-1/3,-1/3,2/3), ncol = 2)
contrasts(pupilChoiceRT$facLoad) = contr.backward.diff
pupilChoiceRT$MZ = ifelse(pupilChoiceRT$zyg14==1, 1, 0)
pupilChoiceRT$site_v2rev = ifelse(pupilChoiceRT$site_v2rev==1, 1, 0)
pupilChoiceRT$Device = factor(pupilChoiceRT$LR_Device)
pupilChoiceRT$acamedbin = ifelse(pupilChoiceRT$acamedtot==0, 0, 1)

# Center continuous variables to interpret intercept at mean value (rather than 0).
# Subject specific variables centered at subject level, trial specific variables centered at trial level.
contTrialVars = c("PCA","pctPCA","adjPCA")
contSubjVars = c("age_v2","afqtpcttran_v2","DSFMAX_v2")

# Center trial specific variables
for (x in contTrialVars) {
  newcol = paste0('c.',x)
  pupilChoiceRT[[newcol]] = as.numeric(scale(pupilChoiceRT[[x]], center=TRUE, scale=FALSE))
}

# Center subject specific variables
subjDF = pupilChoiceRT[c("vetsaid",contSubjVars)]
subjDF %<>% group_by(vetsaid) %>% dplyr::summarise_each(funs(mean))
nums <- sapply(subjDF, is.numeric)
c.subjDF = as.data.frame(apply(subjDF[,nums],2, function(y) y - mean(y, na.rm=TRUE)))
names(c.subjDF) = paste0("c.",names(c.subjDF))
c.subjDF$vetsaid = subjDF$vetsaid
pupilChoiceRT = left_join(pupilChoiceRT, c.subjDF, by="vetsaid")

# Create quantile groups of log CRP
pupilChoiceRT %<>%
  group_by(vetsaid) %>%
  dplyr::summarise(log_meanRT = mean(log_meanRT),
                   log_medianRT = mean(log_medianRT),
                   log_stdRT = mean(log_stdRT),
                   resid_log_stdRT = mean(resid_log_stdRT),
                   log_cvRT = mean(log_cvRT),
                   log_trim_meanRT = mean(log_trim_meanRT)) %>%
  mutate(q.log_meanRT = quantcut(log_meanRT, q=4, labels=seq(1,4)),
         q.log_medianRT = quantcut(log_medianRT, q=4, labels=seq(1,4)),
         q.log_stdRT = quantcut(log_stdRT, q=4, labels=seq(1,4)),
         q.resid_log_stdRT = quantcut(resid_log_stdRT, q=4, labels=seq(1,4)),
         q.log_cvRT = quantcut(log_cvRT, q=4, labels=seq(1,4)),
         q.log_trim_meanRT = quantcut(log_trim_meanRT, q=4, labels=seq(1,4))) %>%
  dplyr::select(vetsaid,q.log_meanRT,q.log_medianRT,q.log_stdRT,
                q.resid_log_stdRT,q.log_cvRT,q.log_trim_meanRT) %>%
  inner_join(pupilChoiceRT, by="vetsaid")

# Create residPCA by regressing BaselineDiameter from PCA and taking the residuals.
lme.PCA.resid = lmer(PCA ~ BaselineDiameter + (1 | case/vetsaid),
                     data=pupilChoiceRT)
pupilChoiceRT$residPCA = resid(lme.PCA.resid)
```

Plot pctPCA and residPCA data to check for ceiling effects on pupil dilation
```{r}
pctPcaPlot = ggplot(pupilChoiceRT, aes(x=pctPCA)) + 
  geom_histogram(fill="steel blue",color="gray") + 
  facet_wrap(~ Load, nrow=3) + 
  ggtitle("Histogram of pctPCA by Load") + 
  xlab("% PCA") + theme_bw() 

residPcaPlot = ggplot(pupilChoiceRT, aes(x=residPCA)) + 
  geom_histogram(fill="steel blue",color="gray") + 
  facet_wrap(~ Load, nrow=3) + 
  ggtitle("Histogram of residPCA by Load") + 
  xlab("PCA (adjusted for baseline)") + theme_bw() 

grid.arrange(pctPcaPlot, residPcaPlot, ncol=2)
```

```{r, include=FALSE}
# Save out figure
pcaGrob = arrangeGrob(pctPcaPlot, residPcaPlot, ncol=2)
ggsave("K:/ReactionTime/results/PCAxLoad.pdf", pcaGrob)
```

Plot histograms of RT measures
```{r}
rtSubset = pupilChoiceRT %>%
  filter(Load==3) %>%
  dplyr::select(log_meanRT, log_trim_meanRT, log_medianRT, 
                log_stdRT, resid_log_stdRT, log_cvRT)

plot_list = list()
for (i in 1:ncol(rtSubset)) {
  p = ggplot(rtSubset,aes_string(x = rtSubset[i])) +
        geom_histogram(fill="steelblue",color="gray") + xlab(names(rtSubset[i]))
  plot_list[[i]] = p
}
do.call(grid.arrange, c(plot_list, list(ncol=2)))
```

```{r, include=FALSE}
g = do.call(arrangeGrob,  c(plot_list, list(ncol=2)))
ggsave("K:/ReactionTime/results/rtHists.pdf", g)
```

Plot pupil dilation of all RT measure quantile groups
```{r}
rtMeasures = c("log_meanRT","log_trim_meanRT","log_medianRT",
               "log_stdRT","resid_log_stdRT","log_cvRT")
measureList = list()
for (measure in rtMeasures){
  measureList[[measure]] = summarySEwithin(pupilChoiceRT, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load", 
                betweenvars=paste0("q.",measure),
                na.rm=TRUE)
}

q.rtMeasures = paste("q",rtMeasures, sep=".")
plot_list = list()
for (i in 1:length(q.rtMeasures)) {
  p = ggplot(measureList[[i]], aes_string(x="Load",y="residPCA", 
                              color=q.rtMeasures[i], group=q.rtMeasures[i])) +
    geom_line() + 
    geom_errorbar(width=.1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
    ggtitle(paste0("Pupil dilation by ",q.rtMeasures[i]," quantile")) +
    theme_bw() + ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
    scale_color_discrete(name=paste0(rtMeasures[i],"\nquantile"),
                         labels=c("Lower","Upper"))
  plot_list[[i]] = p
}
do.call(grid.arrange, c(plot_list, list(ncol=2)))

```

```{r, include=FALSE}
g = do.call(arrangeGrob,  c(plot_list, list(ncol=2)))
ggsave("K:/ReactionTime/results/PCAxLoadxChoiceRT_allGroups.pdf", g,
        width=12,height=10)
```

```{r, include=FALSE}
##Plot pupil dilation of upper and lower RT measure quantile groups
# plot_list = list()
# for (i in 1:length(q.rtMeasures)) {
#   call <- substitute(filter(summarydf, target==1 | target==4),
#                          list(summarydf = measureList[[i]],
#                               target = as.name(q.rtMeasures[[i]]))) 
#   df = eval(call) 
#   p = ggplot(df, aes_string(x="Load",y="residPCA", 
#                               color=q.rtMeasures[i], group=q.rtMeasures[i])) +
#     geom_line() + 
#     geom_errorbar(width=.1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
#     ggtitle(paste0("Pupil dilation by ",q.rtMeasures[i]," quantile")) +
#     theme_bw() + ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
#     scale_color_discrete(name=paste0(rtMeasures[i],"\nquantile"),
#                          labels=c("Lower","Upper"))
#   plot_list[[i]] = p
# }
# do.call(grid.arrange, c(plot_list, list(ncol=2)))

```

```{r, include=FALSE}
# g = do.call(arrangeGrob,  c(plot_list, list(ncol=2)))
# ggsave("K:/ReactionTime/results/PCAxLoadxChoiceRT_Quartiles.pdf", g, 
#         width=12, height=10)
```

Run basic model testing interaction of Load with log mean RT
```{r}
contrasts.facLoad.log_meanRT = rbind(
    'Load3:log_meanRT vs Load6:log_meanRT' = c(0,0,0,0,0,0,0,0,0,0,0,1,0),
    'Load6:log_meanRT vs Load9:log_meanRT' = c(0,0,0,0,0,0,0,0,0,0,0,-1,1),
    'Load3:log_meanRT vs Load9:log_meanRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,1)
)
lme.facLoad.log_meanRT = lmer(residPCA ~ facLoad*log_meanRT + apoe4 + c.age_v2 + 
                            site_v2rev + Device + acamedbin + (1 | case/vetsaid), 
                          data=pupilChoiceRT)
summary(lme.facLoad.log_meanRT)
summary(glht(lme.facLoad.log_meanRT, contrasts.facLoad.log_meanRT), 
              test = adjusted("none"))
```

Run basic model testing interaction of Load with log median RT
```{r}
contrasts.facLoad.log_medianRT = rbind(
    'Load3:log_medianRT vs Load6:log_medianRT' = c(0,0,0,0,0,0,0,0,0,0,0,1,0),
    'Load6:log_medianRT vs Load9:log_medianRT' = c(0,0,0,0,0,0,0,0,0,0,0,-1,1),
    'Load3:log_medianRT vs Load9:log_medianRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,1)
)
lme.facLoad.log_medianRT = lmer(residPCA ~ facLoad*log_medianRT + apoe4 + 
                                  c.age_v2 + site_v2rev + Device + acamedbin + 
                                  (1 | case/vetsaid), data=pupilChoiceRT)
summary(lme.facLoad.log_medianRT)
summary(glht(lme.facLoad.log_medianRT, contrasts.facLoad.log_medianRT), 
              test = adjusted("none"))
```

Run basic model testing interaction of Load with log standard deviation RT
```{r}
contrasts.facLoad.log_stdRT = rbind(
    'Load3:log_stdRT vs Load6:log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,1,0),
    'Load6:log_stdRT vs Load9:log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,-1,1),
    'Load3:log_stdRT vs Load9:log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,1)
)
lme.facLoad.log_stdRT = lmer(residPCA ~ facLoad*log_stdRT + apoe4 + c.age_v2 + 
                            site_v2rev + Device + acamedbin + (1 | case/vetsaid), 
                          data=pupilChoiceRT)
summary(lme.facLoad.log_stdRT)
summary(glht(lme.facLoad.log_stdRT, contrasts.facLoad.log_stdRT), 
              test = adjusted("none"))
```

Run basic model testing interaction of Load with residual log standard deviation RT
```{r}
contrasts.facLoad.resid_log_stdRT = rbind(
    'Load3:resid_log_stdRT vs Load6:resid_log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,1,0),
    'Load6:resid_log_stdRT vs Load9:resid_log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,-1,1),
    'Load3:resid_log_stdRT vs Load9:resid_log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,1)
)
lme.facLoad.resid_log_stdRT = lmer(residPCA ~ facLoad*resid_log_stdRT + 
                                   apoe4 + c.age_v2 + site_v2rev + Device +
                                   acamedbin + (1 | case/vetsaid),
                                   data=pupilChoiceRT)
summary(lme.facLoad.resid_log_stdRT)
summary(glht(lme.facLoad.resid_log_stdRT, contrasts.facLoad.resid_log_stdRT), 
              test = adjusted("none"))
```

Run basic model testing interaction of Load with log coeffient of variance RT
```{r}
contrasts.facLoad.log_cvRT = rbind(
    'Load3:log_cvRT vs Load6:log_cvRT' = c(0,0,0,0,0,0,0,0,0,0,0,1,0),
    'Load6:log_cvRT vs Load9:log_cvRT' = c(0,0,0,0,0,0,0,0,0,0,0,-1,1),
    'Load3:log_cvRT vs Load9:log_cvRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,1)
)
lme.facLoad.log_cvRT = lmer(residPCA ~ facLoad*log_cvRT + apoe4 + c.age_v2 + 
                            site_v2rev + Device + acamedbin + (1 | case/vetsaid), 
                          data=pupilChoiceRT)
summary(lme.facLoad.log_cvRT)
summary(glht(lme.facLoad.log_cvRT, contrasts.facLoad.log_cvRT), 
              test = adjusted("none"))
```

Save out analysis dataset
```{r, include=FALSE}
write.csv(pupilChoiceRT, "K:/ReactionTime/data/pupilDS_ChoiceRT_AnalysisDataset.csv")
```

```{r}
print(sessionInfo(), locale = FALSE)
```