---
title: "Pupillometry and Choice Reaction Time"
author: "Jeremy Elman"
date: "`r Sys.Date()`"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

Load libraries
```{r results='hide', message=FALSE, warning=FALSE}
library(ggplot2)
library(gridExtra)
library(gtools)
library(lme4)
library(arm)
library(lmerTest)
library(dplyr)
library(magrittr)
library(sjPlot)
library(sjmisc)
library(multcomp)
source("K:/code/summarySE.R")
source("K:/code/normDataWithin.R")
source("K:/code/summarySEwithin.R")
source("K:/code/get_legend.R")
```

Load data.
```{r}
pupilChoiceRT = read.csv("K:/Experiments/Pupil_ReactionTime/data/pupil_choiceRT.csv", 
                         stringsAsFactors = FALSE)
pupilChoiceRT = pupilChoiceRT[!is.na(pupilChoiceRT$PCA) &
                              !is.na(pupilChoiceRT$rMCI_cons_v2),]
pupilChoiceRT = subset(pupilChoiceRT, vetsa2=='vetsa2')
str(pupilChoiceRT)
```

Recode two-level factors to 0/1. Center continuous data.
*TRANSFORM*
```{r}
# Create factors
pupilChoiceRT$facLoad = factor(pupilChoiceRT$Load)
pupilChoiceRT$facLoad = relevel(pupilChoiceRT$facLoad, ref="6")
contr.backward.diff = matrix(c(-2/3, 1/3, 1/3,-1/3,-1/3,2/3), ncol = 2)
contrasts(pupilChoiceRT$facLoad) = contr.backward.diff
pupilChoiceRT$MZ = ifelse(pupilChoiceRT$zyg14==1, 1, 0)
pupilChoiceRT$site_v2rev = ifelse(pupilChoiceRT$site_v2rev==1, 1, 0)
pupilChoiceRT$Device = factor(pupilChoiceRT$LR_Device)
pupilChoiceRT$acamedbin = ifelse(pupilChoiceRT$acamedtot==0, 0, 1)

#Bin MCI data into 0 = No impairment, 1 = Single domain MCI, 2 = Multi-domain MCI.
pupilChoiceRT$rMCI_cons_bin = ifelse(pupilChoiceRT$rMCI_cons_v2==0, 0, 
                                        ifelse(pupilChoiceRT$rMCI_cons_v2==1 | 
                                               pupilChoiceRT$rMCI_cons_v2==2, 1, 2))
pupilChoiceRT$rMCI_cons_bin = factor(pupilChoiceRT$rMCI_cons_bin)

# Center continuous variables to interpret intercept at mean value (rather than 0).
# Subject specific variables centered at subject level, trial specific variables centered at trial level.
contTrialVars = c("PCA","pctPCA","adjPCA")
contSubjVars = c("age_v2","afqtpcttran_v2","DSFMAX_v2")

# Center trial specific variables
for (x in contTrialVars) {
  newcol = paste0('c.',x)
  pupilChoiceRT[[newcol]] = as.numeric(scale(pupilChoiceRT[[x]], center=TRUE, scale=FALSE))
}

# Center subject specific variables
subjDF = pupilChoiceRT[c("vetsaid",contSubjVars)]
subjDF %<>% group_by(vetsaid) %>% dplyr::summarise_each(funs(first))
nums <- sapply(subjDF, is.numeric)
c.subjDF = as.data.frame(apply(subjDF[,nums],2, function(y) y - mean(y, na.rm=TRUE)))
names(c.subjDF) = paste0("c.",names(c.subjDF))
c.subjDF$vetsaid = subjDF$vetsaid
pupilChoiceRT = left_join(pupilChoiceRT, c.subjDF, by="vetsaid")

# Create quantile groups
qVars = c("c.DSFMAX_v2","log_meanRT","log_medianRT","log_stdRT",
          "resid_log_stdRT","log_cvRT")
new.qVars = qVars
names(new.qVars) = paste0("q.",qVars)
pupilChoiceRT %<>%
  group_by(vetsaid) %>%
  dplyr::summarise_each_(funs(mean),qVars) %>%
  mutate_each_(funs(quantcut(.,q=4, labels=seq(1,4))),qVars) %>%
  dplyr::select_("vetsaid"="vetsaid",.dots=new.qVars) %>%
  inner_join(pupilChoiceRT, by="vetsaid")

# Create residPCA by regressing BaselineDiameter from PCA and taking the residuals.
lme.PCA.resid = lmer(PCA ~ BaselineDiameter + (1 | case/vetsaid),
                     data=pupilChoiceRT)
pupilChoiceRT$residPCA = resid(lme.PCA.resid)
```

# Basic sample descriptives
```{r, include=FALSE}
#Create dataset with subject level variables to assess relationships with BOLD variance.

subjDatChoiceRT = pupilChoiceRT %>% 
            dplyr::select(-contains("PCA"),-contains("Load")) %>%
            group_by(vetsaid) %>%
            summarise_each(funs(first))
#write.csv(subjDatChoiceRT, "K:/Experiments/Pupil_ReactionTime/data/ChoiceRT_subjDat.csv")
```

How many subjects?
```{r}
n_distinct(subjDatChoiceRT$vetsaid)
```

How many attrition replacements?
```{r}
dplyr::count(subjDatChoiceRT, vetsa2)
```

How many twin pairs vs unpaired twins? 
```{r}
subjDatChoiceRT %>%
  group_by(case) %>%
  dplyr::summarise(n_twins = n_distinct(vetsaid)) %>%
  dplyr::count(n_twins)
```


How many MZ and DZ pairs? (excludes unpaired subjects)
```{r}
subjDatChoiceRT %>% 
  group_by(case) %>%
  mutate(n_twins = n_distinct(vetsaid)) %>%
  filter(n_twins > 1) %>%
  dplyr::summarise(zyg = mean(zyg14)) %>%
  group_by(zyg) %>%
  dplyr::count(zyg)
```

How many levels of load did subjects complete? Shows number of subjects who completed 1, 2, or 3 levels (corresponding to digit spans of 3, 6, and 9).
```{r}
pupilChoiceRT %>%
  group_by(vetsaid) %>%
  dplyr::summarise(load = n()) %>%
  dplyr::count(load)
```

How many of each MCI group?
```{r}
dplyr::count(subjDatChoiceRT, rMCI_cons_v2)
```

How many of each MCI group binned by single or multi-doman MCI?
```{r}
dplyr::count(subjDatChoiceRT, rMCI_cons_bin)
```

Look at frequencies of MCI measures
```{r}
mci.p1 = sjp.frq(subjDatChoiceRT$rMCI_cons_v2, 
          title="MCI groups",
          axisLabels.x=c("Normal","Single Domain\nNon-amnestic",
                         "Single Domain\nAmnestic","Multi Domain\nNon-Amnestic",
                         "Multi Domain Amnestic"),
          axisLimits.y = c(0,900))

mci.p2 = sjp.frq(subjDatChoiceRT$rMCI_cons_bin, 
          title="Binned MCI groups",
          axisLabels.x=c("Normal","Single Domain MCI","Multi Domain MCI"),
          axisLimits.y = c(0,900))

grid.arrange(mci.p1$plot,mci.p2$plot)
```

```{r, include=FALSE}
pdf("K:/Experiments/Pupil_ReactionTime/results/MCI_groups.pdf", width=8, height=6)
grid.arrange(mci.p1$plot,mci.p2$plot)
dev.off()
```

Plot pctPCA and residPCA data to check for ceiling effects on pupil dilation
```{r}
pctPcaPlot = ggplot(pupilChoiceRT, aes(x=pctPCA)) + 
  geom_histogram(fill="lightlightsteelblue22",color="black") + 
  facet_wrap(~ Load, nrow=3) + 
  ggtitle("Histogram of pctPCA by Load") + 
  xlab("% PCA") + theme_bw() 

residPcaPlot = ggplot(pupilChoiceRT, aes(x=residPCA)) + 
  geom_histogram(fill="lightlightsteelblue22",color="black") + 
  facet_wrap(~ Load, nrow=3) + 
  ggtitle("Histogram of residPCA by Load") + 
  xlab("PCA (adjusted for baseline)") + theme_bw() 

grid.arrange(pctPcaPlot, residPcaPlot, ncol=2)
```


```{r, include=FALSE}
pdf("K:/Experiments/Pupil_ReactionTime/results/Choice/PCAxLoad.pdf")
grid.arrange(pctPcaPlot, residPcaPlot, ncol=2)
dev.off()
```

Plot histograms of RT measures
```{r}
rtSubset = pupilChoiceRT %>%
  filter(Load==3) %>%
  dplyr::select(log_meanRT, log_medianRT, 
                log_stdRT, resid_log_stdRT, log_cvRT)

plot_list = list()
for (i in 1:ncol(rtSubset)) {
  p = ggplot(rtSubset,aes_string(x = rtSubset[i])) +
        geom_histogram(fill="lightlightsteelblue22",color="black") + 
        xlab(names(rtSubset[i])) + theme_bw()
  plot_list[[i]] = p
}


do.call(grid.arrange, c(plot_list, list(ncol=2)))
```

```{r, include=FALSE}
pdf("K:/Experiments/Pupil_ReactionTime/results/Choice/rtHists.pdf")
do.call(grid.arrange, c(plot_list, list(ncol=2)))
dev.off()
```

Plot pupil dilation of all RT measure quantile groups
```{r}
rtMeasures = c("log_meanRT","log_medianRT",
               "log_stdRT","resid_log_stdRT","log_cvRT")
measureList = list()
for (measure in rtMeasures){
  measureList[[measure]] = summarySEwithin(pupilChoiceRT, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load", 
                betweenvars=paste0("q.",measure),
                na.rm=TRUE)
}

q.rtMeasures = paste("q",rtMeasures, sep=".")
plot_list = list()
for (i in 1:length(q.rtMeasures)) {
  p = ggplot(measureList[[i]], aes_string(x="Load",y="residPCA", 
                              color=q.rtMeasures[i], group=q.rtMeasures[i])) +
    geom_line() + 
    geom_errorbar(width=.1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
    ggtitle(paste0("Pupil dilation by ",q.rtMeasures[i]," quantile")) +
    theme_bw(14) + ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
    scale_color_discrete(name="quantile")
  plot_list[[i]] = p
}

legend = get_legend(plot_list[[1]])
for (i in 1:length(plot_list)) {
  plot_list[[i]] = plot_list[[i]] + theme(legend.position="none")
}
plot_list$legend = legend

#Save out plot
pdf("K:/Experiments/Pupil_ReactionTime/results/Choice/PCAxLoadxChoiceRT_allGroups.pdf",width=12,height=10)
do.call(grid.arrange,  c(plot_list, list(ncol=2)))
dev.off()
```


```{r, include=FALSE}
#Plot pupil dilation of upper and lower RT measure quantile groups
plot_list = list()
for (i in 1:length(q.rtMeasures)) {
  call <- substitute(filter(summarydf, target==1 | target==4),
                         list(summarydf = measureList[[i]],
                              target = as.name(q.rtMeasures[[i]]))) 
  df = eval(call) 
  p = ggplot(df, aes_string(x="Load",y="residPCA", 
                              color=q.rtMeasures[i], group=q.rtMeasures[i])) +
    geom_line() + 
    geom_errorbar(width=.1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
    ggtitle(paste0("Pupil dilation by ",q.rtMeasures[i]," quantile")) +
    theme_bw(14) + ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
    scale_color_discrete(name=paste0(rtMeasures[i],"\nquantile"),
                         labels=c("Lower","Upper"))
  plot_list[[i]] = p
}

legend = get_legend(plot_list[[1]])
for (i in 1:length(plot_list)) {
  plot_list[[i]] = plot_list[[i]] + theme(legend.position="none")
}
plot_list$legend = legend

# Save out plot
pdf("K:/Experiments/Pupil_ReactionTime/results/Choice/PCAxLoadxChoiceRT_Quartiles.pdf",width=12,height=10)
do.call(grid.arrange,  c(plot_list, list(ncol=2)))
dev.off()
```

-------------------------------
# Mixed Effects Models: Cognitively normal only

```{r, include=FALSE}
# Levels of load to test
loads = c(3,6,9)
```

**Log Mean RT**
```{r, echo=FALSE}
plot_list[[1]]
```

Run basic model testing interaction of Load with log mean RT
```{r}
contrasts.facLoad.log_meanRT = rbind(
    'Load3:log_meanRT vs Load6:log_meanRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0),
    'Load6:log_meanRT vs Load9:log_meanRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),
    'Load3:log_meanRT vs Load9:log_meanRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0)
)
lme.facLoad.log_meanRT = lmer(residPCA ~ facLoad*(log_meanRT + c.DSFMAX_v2) + 
                                apoe4 + c.age_v2 + site_v2rev + Device + 
                                acamedbin + c.afqtpcttran_v2 + 
                                (1 | case/vetsaid),
                                data=subset(pupilChoiceRT,rMCI_cons_bin==0))
summary(lme.facLoad.log_meanRT)
summary(glht(lme.facLoad.log_meanRT, contrasts.facLoad.log_meanRT), 
              test = adjusted("none"))
```

Test for differences based on mean RT within each level of Load
```{r}
lme.log_meanRT.loads <- lapply(loads, function(x) {
    lmer(residPCA ~ log_meanRT + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + c.afqtpcttran_v2 + 
                    (1 | case), data=subset(pupilChoiceRT,Load==x &
                                              rMCI_cons_bin==0))
})
lapply(lme.log_meanRT.loads, summary)
```

**Log Median RT**
```{r, echo=FALSE}
plot_list[[2]]
```

Run basic model testing interaction of Load with log median RT
```{r}
contrasts.facLoad.log_medianRT = rbind(
    'Load3:log_medianRT vs Load6:log_medianRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0),
    'Load6:log_medianRT vs Load9:log_medianRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),
    'Load3:log_medianRT vs Load9:log_medianRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0)
)
lme.facLoad.log_medianRT = lmer(residPCA ~ facLoad*(log_medianRT + c.DSFMAX_v2) + 
                                apoe4 + c.age_v2 + site_v2rev + Device + 
                                acamedbin + c.afqtpcttran_v2 + 
                                (1 | case/vetsaid),
                                data=subset(pupilChoiceRT,rMCI_cons_bin==0))
summary(lme.facLoad.log_medianRT)
summary(glht(lme.facLoad.log_medianRT, contrasts.facLoad.log_medianRT), 
              test = adjusted("none"))
```

Test for differences based on median RT within each level of Load
```{r}
lme.log_medianRT.loads <- lapply(loads, function(x) {
    lmer(residPCA ~ log_medianRT + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + c.afqtpcttran_v2 + 
                    (1 | case), data=subset(pupilChoiceRT,Load==x & 
                                              rMCI_cons_bin==0))
})
lapply(lme.log_medianRT.loads, summary)
```

**Log Standard Deviation RT**
```{r, echo=FALSE}
plot_list[[3]]
```

Run basic model testing interaction of Load with log standard deviation RT
```{r}
contrasts.facLoad.log_stdRT = rbind(
    'Load3:log_stdRT vs Load6:log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0),
    'Load6:log_stdRT vs Load9:log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),
    'Load3:log_stdRT vs Load9:log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0)
)
lme.facLoad.log_stdRT = lmer(residPCA ~ facLoad*(log_stdRT + c.DSFMAX_v2) + 
                                apoe4 + c.age_v2 + site_v2rev + Device + 
                                acamedbin + c.afqtpcttran_v2 + 
                                (1 | case/vetsaid),
                                data=subset(pupilChoiceRT,rMCI_cons_bin==0))
summary(lme.facLoad.log_stdRT)
summary(glht(lme.facLoad.log_stdRT, contrasts.facLoad.log_stdRT), 
              test = adjusted("none"))
```

Test for differences based on standard deviation RT within each level of Load
```{r}
lme.log_stdRT.loads <- lapply(loads, function(x) {
    lmer(residPCA ~ log_stdRT + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + c.afqtpcttran_v2 + 
                    (1 | case), data=subset(pupilChoiceRT,Load==x & 
                                              rMCI_cons_bin==0))
})
lapply(lme.log_stdRT.loads, summary)
```

**Log Residual Standard Deviation RT**
```{r, echo=FALSE}
plot_list[[4]]
```

Run basic model testing interaction of Load with residual log standard deviation RT
```{r}
contrasts.facLoad.resid_log_stdRT = rbind(
    'Load3:resid_log_stdRT vs Load6:resid_log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0),
    'Load6:resid_log_stdRT vs Load9:resid_log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),
    'Load3:resid_log_stdRT vs Load9:resid_log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0)
)
lme.facLoad.resid_log_stdRT = lmer(residPCA ~ facLoad*(resid_log_stdRT + c.DSFMAX_v2) + 
                                apoe4 + c.age_v2 + site_v2rev + Device + 
                                acamedbin + c.afqtpcttran_v2 + 
                                (1 | case/vetsaid),
                                data=subset(pupilChoiceRT,rMCI_cons_bin==0))
summary(lme.facLoad.resid_log_stdRT)
summary(glht(lme.facLoad.resid_log_stdRT, contrasts.facLoad.resid_log_stdRT), 
              test = adjusted("none"))
```

Test for differences based on residual standard deviation RT within each level of Load
```{r}
lme.resid_log_stdRT.loads <- lapply(loads, function(x) {
    lmer(residPCA ~ resid_log_stdRT + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + c.afqtpcttran_v2 + 
                    (1 | case), data=subset(pupilChoiceRT,Load==x & 
                                              rMCI_cons_bin==0))
})
lapply(lme.resid_log_stdRT.loads, summary)
```

**Log Coefficient of Variation RT**
```{r, echo=FALSE}
plot_list[[5]]
```

Run basic model testing interaction of Load with log coeffient of variance RT
```{r}
contrasts.facLoad.log_cvRT = rbind(
    'Load3:log_cvRT vs Load6:log_cvRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0),
    'Load6:log_cvRT vs Load9:log_cvRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),
    'Load3:log_cvRT vs Load9:log_cvRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0)
)
lme.facLoad.log_cvRT = lmer(residPCA ~ facLoad*(log_cvRT + c.DSFMAX_v2) + 
                                apoe4 + c.age_v2 + site_v2rev + Device + 
                                acamedbin + c.afqtpcttran_v2 + 
                                (1 | case/vetsaid),
                                data=subset(pupilChoiceRT,rMCI_cons_bin==0))
summary(lme.facLoad.log_cvRT)
summary(glht(lme.facLoad.log_cvRT, contrasts.facLoad.log_cvRT), 
              test = adjusted("none"))
```

Test for differences based on coeffiecient of variation RT within each level of Load
```{r}
lme.log_cvRT.loads <- lapply(loads, function(x) {
    lmer(residPCA ~ log_cvRT + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + c.afqtpcttran_v2 + 
                    (1 | case), data=subset(pupilChoiceRT,Load==x &
                                              rMCI_cons_bin==0))
})
lapply(lme.log_cvRT.loads, summary)
```

----------------
# Mixed Effects Models: All MCI groups

Run model testing interaction of Load with log mean RT, digit span and MCI
```{r}
contrasts.facLoad.log_meanRT.MCI = rbind(
    'Load3:log_meanRT vs Load6:log_meanRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,0,0,0),
    'Load6:log_meanRT vs Load9:log_meanRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
    'Load3:log_meanRT vs Load9:log_meanRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0)
)

lme.facLoad.log_meanRT.MCI = lmer(residPCA ~ facLoad*(log_meanRT + 
                                                        c.DSFMAX_v2 +
                                                        rMCI_cons_bin) + 
                                    apoe4 + c.age_v2 + site_v2rev + 
                                    Device + acamedbin + c.afqtpcttran_v2 + 
                                    (1 | case/vetsaid), data=pupilChoiceRT)
summary(lme.facLoad.log_meanRT.MCI)
summary(glht(lme.facLoad.log_meanRT.MCI, 
             contrasts.facLoad.log_meanRT.MCI),
             test = adjusted("none"))
```

Test for differences based on mean RT within each level of Load
```{r}
lme.log_meanRT.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ log_meanRT + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + 
                    rMCI_cons_bin + c.afqtpcttran_v2 + 
                    (1 | case), 
         data=filter(pupilChoiceRT, Load==x))
})
lapply(lme.log_meanRT.loads.MCI, summary)
```

Run model testing interaction of Load with log median RT, digit span and MCI
```{r}
contrasts.facLoad.log_medianRT.MCI = rbind(
    'Load3:log_medianRT vs Load6:log_medianRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,0,0,0),
    'Load6:log_medianRT vs Load9:log_medianRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
    'Load3:log_medianRT vs Load9:log_medianRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0)
)

lme.facLoad.log_medianRT.MCI = lmer(residPCA ~ facLoad*(log_medianRT + 
                                                        c.DSFMAX_v2 +
                                                        rMCI_cons_bin) + 
                                    apoe4 + c.age_v2 + site_v2rev + 
                                    Device + acamedbin + c.afqtpcttran_v2 + 
                                    (1 | case/vetsaid), data=pupilChoiceRT)
summary(lme.facLoad.log_medianRT.MCI)
summary(glht(lme.facLoad.log_medianRT.MCI, 
             contrasts.facLoad.log_medianRT.MCI),
             test = adjusted("none"))
```

Test for differences based on median RT within each level of Load
```{r}
lme.log_medianRT.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ log_medianRT + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + 
                    rMCI_cons_bin + c.afqtpcttran_v2 + 
                    (1 | case), 
         data=filter(pupilChoiceRT, Load==x))
})
lapply(lme.log_medianRT.loads.MCI, summary)
```

Run model testing interaction of Load with log std RT, digit span and MCI
```{r}
contrasts.facLoad.log_stdRT.MCI = rbind(
    'Load3:log_stdRT vs Load6:log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,0,0,0),
    'Load6:log_stdRT vs Load9:log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
    'Load3:log_stdRT vs Load9:log_stdRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0)
)

lme.facLoad.log_stdRT.MCI = lmer(residPCA ~ facLoad*(log_stdRT + 
                                                        c.DSFMAX_v2 +
                                                        rMCI_cons_bin) + 
                                    apoe4 + c.age_v2 + site_v2rev + 
                                    Device + acamedbin + c.afqtpcttran_v2 + 
                                    (1 | case/vetsaid), data=pupilChoiceRT)
summary(lme.facLoad.log_stdRT.MCI)
summary(glht(lme.facLoad.log_stdRT.MCI, 
             contrasts.facLoad.log_stdRT.MCI),
             test = adjusted("none"))
```

Test for differences based on std RT within each level of Load
```{r}
lme.log_stdRT.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ log_stdRT + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + 
                    rMCI_cons_bin + c.afqtpcttran_v2 + 
                    (1 | case), 
         data=filter(pupilChoiceRT, Load==x))
})
lapply(lme.log_stdRT.loads.MCI, summary)
```

Run model testing interaction of Load with log cv RT, digit span and MCI
```{r}
contrasts.facLoad.log_cvRT.MCI = rbind(
    'Load3:log_cvRT vs Load6:log_cvRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,0,0,0),
    'Load6:log_cvRT vs Load9:log_cvRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
    'Load3:log_cvRT vs Load9:log_cvRT' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0)
)

lme.facLoad.log_cvRT.MCI = lmer(residPCA ~ facLoad*(log_cvRT + 
                                                        c.DSFMAX_v2 +
                                                        rMCI_cons_bin) + 
                                    apoe4 + c.age_v2 + site_v2rev + 
                                    Device + acamedbin + c.afqtpcttran_v2 + 
                                    (1 | case/vetsaid), data=pupilChoiceRT)
summary(lme.facLoad.log_cvRT.MCI)
summary(glht(lme.facLoad.log_cvRT.MCI, 
             contrasts.facLoad.log_cvRT.MCI),
             test = adjusted("none"))
```

Test for differences based on cv RT within each level of Load
```{r}
lme.log_cvRT.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ log_cvRT + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + 
                    rMCI_cons_bin + c.afqtpcttran_v2 + 
                    (1 | case), 
         data=filter(pupilChoiceRT, Load==x))
})
lapply(lme.log_cvRT.loads.MCI, summary)
```

----------------------------
# Covariate Plots 

Plot pupil dilation by digit span max quantile
```{r, echo=FALSE}
summaryResidPCA.DSFMAX_v2 = summarySEwithin(pupilChoiceRT, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load",
                betweenvars="q.c.DSFMAX_v2",
                na.rm=TRUE)
  
p.DSFMAX_v2 = summaryResidPCA.DSFMAX_v2 %>%
          filter(q.c.DSFMAX_v2==1 | q.c.DSFMAX_v2==4) %>%
          ggplot(., aes(x=Load,y=residPCA,
                        color=q.c.DSFMAX_v2,
                        group=q.c.DSFMAX_v2)) +
            geom_line() +
            geom_errorbar(width=.1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
            ggtitle("Max digit span") + theme_bw(16) +
            ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
            scale_color_discrete(name="Max digit span\nquantile",
                                 labels=c("Lower","Upper"))
print(p.DSFMAX_v2)
ggsave("K:/Experiments/Pupil_ReactionTime/results/pupil_MaxDigitSpan.pdf", p.DSFMAX_v2)
```

Plot pupil dilation by digit span max quantile
```{r, echo=FALSE}
summaryResidPCA.MCI = summarySEwithin(pupilChoiceRT, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load",
                betweenvars="rMCI_cons_bin",
                na.rm=TRUE)
  
p.MCI = summaryResidPCA.MCI %>%
          ggplot(., aes(x=Load,y=residPCA,
                        color=rMCI_cons_bin,
                        group=rMCI_cons_bin)) +
            geom_line() +
            geom_errorbar(width=.1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
            ggtitle("MCI Status") + theme_bw(16) +
            ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
            scale_color_discrete(name="MCI Group", 
                                 labels=c("No MCI",
                                          "Single Domain MCI",
                                          "Multi-Domain MCI"))
print(p.MCI)
ggsave("K:/AX-CPT/results/pupil_MCI.pdf", p.MCI)
```
----------------------------

```{r, include=FALSE}
#Save out analysis dataset
write.csv(pupilChoiceRT,
          "K:/Experiments/Pupil_ReactionTime/data/pupilDS_ChoiceRT_AnalysisDataset.csv")
```

```{r}
print(sessionInfo(), locale = FALSE)
```