---
title: "Pupillometry and Simple Reaction Time"
author: "Jeremy Elman"
date: "`r Sys.Date()`"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

Load libraries
```{r results='hide', message=FALSE, warning=FALSE}
library(ggplot2)
library(gridExtra)
library(gtools)
library(lme4)
library(arm)
library(lmerTest)
library(dplyr)
library(magrittr)
library(sjPlot)
library(sjmisc)
library(multcomp)
source("K:/code/summarySE.R")
source("K:/code/normDataWithin.R")
source("K:/code/summarySEwithin.R")
```

Load data.
```{r}
pupilSimpleRT = read.csv("K:/ReactionTime/data/pupil_simpleRT.csv", 
                         stringsAsFactors = FALSE)
pupilSimpleRT = pupilSimpleRT[!is.na(pupilSimpleRT$PCA),]
str(pupilSimpleRT)
```

How many subjects?
```{r}
n_distinct(pupilSimpleRT$vetsaid)
```

How many attrition replacements?
```{r}
pupilSimpleRT %>% 
  group_by(vetsaid) %>% 
  dplyr::summarise(AR = first(vetsa2)) %>%
  group_by(AR) %>%
  dplyr::summarise(n=n())
```

How many twin pairs vs unpaired twins? 
```{r}
pupilSimpleRT %>%
  group_by(case) %>%
  dplyr::summarise(n_twins = n_distinct(vetsaid)) %>%
  group_by(n_twins) %>%
  dplyr::summarise(n=n())
```


How many MZ and DZ pairs? (excludes unpaired subjects)
```{r}
pupilSimpleRT %>% 
  group_by(case) %>%
  mutate(n_twins = n_distinct(vetsaid)) %>%
  filter(n_twins > 1) %>%
  dplyr::summarise(zyg = mean(zyg14)) %>%
  group_by(zyg) %>%
  dplyr::count(zyg)
```

How many levels of load did subjects complete? Shows number of subjects who completed 1, 2, or 3 levels (corresponding to digit spans of 3, 6, and 9).
```{r}
pupilSimpleRT %>%
  group_by(vetsaid) %>%
  dplyr::summarise(load = n()) %>%
  dplyr::count(load)
```

Recode two-level factors to 0/1. Center continuous data.
*TRANSFORM*
```{r}
# Create factors
pupilSimpleRT$facLoad = factor(pupilSimpleRT$Load)
contr.backward.diff = matrix(c(-2/3, 1/3, 1/3,-1/3,-1/3,2/3), ncol = 2)
contrasts(pupilSimpleRT$facLoad) = contr.backward.diff
pupilSimpleRT$MZ = ifelse(pupilSimpleRT$zyg14==1, 1, 0)
pupilSimpleRT$site_v2rev = ifelse(pupilSimpleRT$site_v2rev==1, 1, 0)
pupilSimpleRT$Device = factor(pupilSimpleRT$LR_Device)
pupilSimpleRT$acamedbin = ifelse(pupilSimpleRT$acamedtot==0, 0, 1)

# Center continuous variables to interpret intercept at mean value (rather than 0).
# Subject specific variables centered at subject level, trial specific variables centered at trial level.
contTrialVars = c("PCA","pctPCA","adjPCA")
contSubjVars = c("age_v2","afqtpcttran_v2","DSFMAX_v2")

# Center trial specific variables
for (x in contTrialVars) {
  newcol = paste0('c.',x)
  pupilSimpleRT[[newcol]] = as.numeric(scale(pupilSimpleRT[[x]], center=TRUE, scale=FALSE))
}

# Center subject specific variables
subjDF = pupilSimpleRT[c("vetsaid",contSubjVars)]
subjDF %<>% group_by(vetsaid) %>% dplyr::summarise_each(funs(mean))
nums <- sapply(subjDF, is.numeric)
c.subjDF = as.data.frame(apply(subjDF[,nums],2, function(y) y - mean(y, na.rm=TRUE)))
names(c.subjDF) = paste0("c.",names(c.subjDF))
c.subjDF$vetsaid = subjDF$vetsaid
pupilSimpleRT = left_join(pupilSimpleRT, c.subjDF, by="vetsaid")

# Create quantile groups of log CRP
pupilSimpleRT %<>%
  group_by(vetsaid) %>%
  dplyr::summarise(mean = mean(log.CRP_v2)) %>%
  mutate(q.log.CRP_v2 = quantcut(mean, labels=seq(1,4))) %>%
  dplyr::select(vetsaid, q.log.CRP_v2) %>%
  inner_join(pupilSimpleRT, by="vetsaid")

# Create residPCA by regressing BaselineDiameter from PCA and taking the residuals.
lme.PCA.resid = lmer(PCA ~ BaselineDiameter + (1 | case/vetsaid), data=pupilSimpleRT)
pupilSimpleRT$residPCA = resid(lme.PCA.resid)
```


Plot pctPCA and residPCA data to check for ceiling effects on pupil dilation
```{r}
pctPcaPlot = ggplot(pupilSimpleRT, aes(x=pctPCA)) + 
  geom_histogram(fill="steel blue",color="gray") + 
  facet_wrap(~ Load, nrow=3) + 
  ggtitle("Histogram of pctPCA by Load") + 
  xlab("% PCA") + theme_bw() 

residPcaPlot = ggplot(pupilSimpleRT, aes(x=residPCA)) + 
  geom_histogram(fill="steel blue",color="gray") + 
  facet_wrap(~ Load, nrow=3) + 
  ggtitle("Histogram of residPCA by Load") + 
  xlab("PCA (adjusted for baseline)") + theme_bw() 

grid.arrange(pctPcaPlot, residPcaPlot, ncol=2)
```

```{r, include=FALSE}
# Save out figure
pcaGrob = arrangeGrob(pctPcaPlot, residPcaPlot, ncol=2)
ggsave("K:/ReactionTime/results/PCAxLoad.pdf", pcaGrob)
```


```{r}
print(sessionInfo(), locale = FALSE)
```