---
title: "Pupillometry and Reaction Time"
author: "Jeremy Elman"
date: "`r Sys.Date()`"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

Load libraries
```{r results='hide', message=FALSE, warning=FALSE}
library(ggplot2)
library(gridExtra)
library(gtools)
library(lme4)
library(arm)
library(lmerTest)
library(dplyr)
library(magrittr)
library(sjPlot)
library(sjmisc)
library(multcomp)
source("~/netshare/K/code/misc/summarySE.R")
source("~/netshare/K/code/misc/normDataWithin.R")
source("~/netshare/K/code/misc/summarySEwithin.R")
source("~/netshare/K/code/misc/get_legend.R")
```

Load data.
```{r}
pupilRT = read.csv("~/netshare/K/Projects/Pupil_ReactionTime/data/pupil_RT.csv", 
                         stringsAsFactors = FALSE)
pupilRT = pupilRT[!is.na(pupilRT$PCA) & !is.na(pupilRT$rMCI_cons_v2pe) & !is.na(pupilRT$CHRTGMEANLOG_V2_nasp),]
pupilRT = subset(pupilRT, (VETSAGRP=='V1V2') | (VETSAGRP=='V2AR'))
str(pupilRT)
```

Recode two-level factors to 0/1. Center continuous data.
*TRANSFORM*
```{r}
# Create factors
pupilRT$facLoad = factor(pupilRT$Load)
pupilRT$facLoad = relevel(pupilRT$facLoad, ref="6")
loads = c("3","6","9")
pupilRT$MZ = ifelse(pupilRT$zygos==1, 1, 0)
pupilRT$site_v2rev = ifelse(pupilRT$site_v2rev==1, 1, 0)
pupilRT$Device = factor(pupilRT$LR_Device)
pupilRT$acamedbin = ifelse(pupilRT$acamedtot==0, 0, 1)

#Bin MCI data into 0 = No impairment, 1 = Single domain MCI, 2 = Multi-domain MCI.
pupilRT$rMCI_cons_3grp = ifelse(pupilRT$rMCI_cons_v2pe==0, 0, 
                                        ifelse(pupilRT$rMCI_cons_v2pe==1 | 
                                               pupilRT$rMCI_cons_v2pe==2, 1, 2))
pupilRT$rMCI_cons_3grp = factor(pupilRT$rMCI_cons_3grp, 
                                   labels=c("CN","SMCI","MMCI"))

#Bin MCI data into 0 = No impairment, 1 = Non-amnestic S-MCI, 2 = Amnestic S-MCI, 3 = Multi-domain MCI.
pupilRT$rMCI_cons_4grp = pupilRT$rMCI_cons_v2pe
pupilRT$rMCI_cons_4grp = gsub(4, 3, pupilRT$rMCI_cons_4grp)
pupilRT$rMCI_cons_4grp = factor(pupilRT$rMCI_cons_4grp,
                                   labels=c("CN","naSMCI","aSMCI","MMCI"))

# Original MCI categories: 0 = No impairment, 1 = Non-amnestic S-MCI, 2 = Amnestic S-MCI, 3 = Non-amnestic M-MCI, 4 = Amnestic M-MCI
pupilRT$rMCI_cons_v2pe = factor(pupilRT$rMCI_cons_v2pe, 
                                   labels=c("CN","naSMCI","aSMCI","naMMCI","aMMCI"))

# Center continuous variables to interpret intercept at mean value (rather than 0).
# Subject specific variables centered at subject level, trial specific variables centered at trial level.

# Trial specific variables
contTrialVars = c("PCA","pctPCA","adjPCA")

# Center trial specific variables
for (x in contTrialVars) {
  newcol = paste0('c.',x)
  pupilRT[[newcol]] = as.numeric(scale(pupilRT[[x]], center=TRUE, scale=FALSE))
}

# Subject specific variables centered at subject level.
contSubjVars = c("age_v2","nas201tran","DSFMAX_V2_nasp")

# Center subject specific variables
subjDF = pupilRT[c("vetsaid",contSubjVars)]
subjDF %<>% group_by(vetsaid) %>% dplyr::summarise_each(funs(mean))
nums <- sapply(subjDF, is.numeric)
c.subjDF = as.data.frame(apply(subjDF[,nums],2, function(y) y - mean(y, na.rm=TRUE)))
names(c.subjDF) = paste0("c.",names(c.subjDF))
c.subjDF$vetsaid = subjDF$vetsaid
pupilRT = left_join(pupilRT, c.subjDF, by="vetsaid")


### Generate new subject level variables ###

# Create subject level dataset of RT variables
subjRT = pupilRT %>%
  select(vetsaid, ends_with("LOG_V2_nasp")) %>%
  group_by(vetsaid) %>%
  summarise_all(funs(first))

# Derive RT metrics such as CV and residSTD
# Coefficient of Variation = STD / MEAN
subjRT = subjRT %>% 
  mutate(SRTLCV_V2_nasp = SRTLSTDLOG_V2_nasp/SRTLMEANLOG_V2_nasp,
         SRTRCV_V2_nasp = SRTRSTDLOG_V2_nasp/SRTRMEANLOG_V2_nasp,
         SRTGCV_V2_nasp = SRTGSTDLOG_V2_nasp/SRTGMEANLOG_V2_nasp,
         CHRTLCV_V2_nasp = CHRTLSTDLOG_V2_nasp/CHRTLMEANLOG_V2_nasp,
         CHRTRCV_V2_nasp = CHRTRSTDLOG_V2_nasp/CHRTRMEANLOG_V2_nasp,
         CHRTGCV_V2_nasp = CHRTGSTDLOG_V2_nasp/CHRTGMEANLOG_V2_nasp)

# Standard deviation orthogonalized with respect to mean
subjRT$residSRTLSTDLOG_V2_nasp = resid(lm(SRTLSTDLOG_V2_nasp ~ SRTLMEANLOG_V2_nasp, data=subjRT, na.action="na.exclude"))
subjRT$residSRTRSTDLOG_V2_nasp = resid(lm(SRTRSTDLOG_V2_nasp ~ SRTRMEANLOG_V2_nasp, data=subjRT, na.action="na.exclude"))
subjRT$residSRTGSTDLOG_V2_nasp = resid(lm(SRTGSTDLOG_V2_nasp ~ SRTGMEANLOG_V2_nasp, data=subjRT, na.action="na.exclude"))
subjRT$residCHRTLSTDLOG_V2_nasp = resid(lm(CHRTLSTDLOG_V2_nasp ~ CHRTLMEANLOG_V2_nasp, data=subjRT, na.action="na.exclude"))
subjRT$residCHRTRSTDLOG_V2_nasp = resid(lm(CHRTRSTDLOG_V2_nasp ~ CHRTRMEANLOG_V2_nasp, data=subjRT, na.action="na.exclude"))
subjRT$residCHRTGSTDLOG_V2_nasp = resid(lm(CHRTGSTDLOG_V2_nasp ~ CHRTGMEANLOG_V2_nasp, data=subjRT, na.action="na.exclude"))

# Merge back into full pupil dataset
pupilRT = pupilRT %>%
    left_join(subjRT, by="vetsaid") %>% 
    dplyr::select(-ends_with(".x"))

names(pupilRT) = gsub(".y","",names(pupilRT), fixed=T)


# Create quantile groups
qVars = names(pupilRT)[grepl("_V2_nasp", names(pupilRT)) & !grepl("c.", names(pupilRT))]
new.qVars = qVars
names(new.qVars) = paste0("q.",qVars)

quantDF = pupilRT %>%
  group_by(vetsaid) %>%
  summarise_at(vars(one_of(qVars)), funs(first)) %>%
  mutate_at(vars(one_of(qVars)), funs(quantcut), labels=seq(1,4)) %>%
  dplyr::select_("vetsaid"="vetsaid",.dots=new.qVars) 
 
pupilRT = pupilRT %>%
  inner_join(quantDF, by="vetsaid")

# Create residPCA by regressing BaselineDiameter from PCA and taking the residuals.
lme.PCA.resid = lmer(PCA ~ BaselineDiameter + (1 | case/vetsaid),
                     data=pupilRT)
pupilRT$residPCA = resid(lme.PCA.resid)
```

# Basic sample descriptives
```{r, include=FALSE}
#Create dataset with subject level variables to assess relationships with BOLD variance.
subjDatRT = pupilRT %>% 
            dplyr::select(-contains("PCA"),-contains("Load")) %>%
            group_by(vetsaid) %>%
            summarise_all(funs(first))
```

How many subjects?
```{r}
n_distinct(subjDatRT$vetsaid)
```

How many attrition replacements?
```{r}
dplyr::count(subjDatRT, VETSAGRP)
```

How many twin pairs vs unpaired twins? 
```{r}
subjDatRT %>%
  group_by(case) %>%
  dplyr::summarise(n_twins = n_distinct(vetsaid)) %>%
  dplyr::count(n_twins)
```


How many MZ and DZ pairs? (excludes unpaired subjects)
```{r}
subjDatRT %>% 
  group_by(case) %>%
  mutate(n_twins = n_distinct(vetsaid)) %>%
  filter(n_twins > 1) %>%
  dplyr::summarise(zyg = mean(zygos)) %>%
  group_by(zyg) %>%
  dplyr::count(zyg)
```

How many levels of load did subjects complete? Shows number of subjects who completed 1, 2, or 3 levels (corresponding to digit spans of 3, 6, and 9).
```{r}
pupilRT %>%
  group_by(vetsaid) %>%
  dplyr::summarise(load = n()) %>%
  dplyr::count(load)
```

How many of each MCI group?
```{r}
dplyr::count(subjDatRT, rMCI_cons_v2pe)
```

How many of each MCI group binned by single or multi-doman MCI?
```{r}
dplyr::count(subjDatRT, rMCI_cons_3grp)
```

How many of each MCI group binned by single amnestic/non-amnestic or multi-doman MCI?
```{r}
dplyr::count(subjDatRT, rMCI_cons_4grp)
```

Plot frequencies of MCI measures
```{r}
sjp.frq(subjDatRT$rMCI_cons_4grp, 
          title="MCI groups",
          axis.labels=c("Normal","Single Domain\nNon-amnestic",
                         "Single Domain\nAmnestic","Multi Domain"))
```


```{r, include=FALSE}
# pdf("~/netshare/K/Projects/Pupil_ReactionTime/results/RT_MCI_groups.pdf", width=8, height=6)
# grid.arrange(mci.p1$plot,mci.p2$plot)
# dev.off()
```

Plot pctPCA and residPCA data to check for ceiling effects on pupil dilation
```{r}
pctPcaPlot = ggplot(pupilRT, aes(x=pctPCA)) + 
  geom_histogram(fill="steelblue3",color="black",size=.4) + 
  facet_wrap(~ Load, nrow=3) + 
  ggtitle("Histogram of pctPCA by Load") + 
  xlab("% PCA") + theme_bw() 

residPcaPlot = ggplot(pupilRT, aes(x=residPCA)) + 
  geom_histogram(fill="steelblue3",color="black",size=.4) + 
  facet_wrap(~ Load, nrow=3) + 
  ggtitle("Histogram of residPCA by Load") + 
  xlab("PCA (adjusted for baseline)") + theme_bw() 

grid.arrange(pctPcaPlot, residPcaPlot, ncol=2)
```


```{r, include=FALSE}
# pdf("~/netshare/K/Projects/Pupil_ReactionTime/results/Choice_PCAxLoad.pdf")
# grid.arrange(pctPcaPlot, residPcaPlot, ncol=2)
# dev.off()
```

Plot histograms of RT measures
```{r}
rtSubset = pupilRT %>%
  filter(Load==3) %>%
  dplyr::select(contains("CHRTG"), contains("SRTG"), -starts_with("q."))

plot_list = list()
for (i in 1:ncol(rtSubset)) {
  p = ggplot(rtSubset,aes_string(x = rtSubset[[i]])) +
        geom_histogram(fill="steelblue3",color="black",size=.4) + 
        xlab(names(rtSubset[i])) + theme_bw()
  plot_list[[i]] = p
}


do.call(grid.arrange, c(plot_list, list(nrow=4)))
```

```{r, include=FALSE}
# pdf("~/netshare/K/Projects/Pupil_ReactionTime/results/Choice_rtHists.pdf")
# do.call(grid.arrange, c(plot_list, list(ncol=2)))
# dev.off()
```

```{r}
### Create function to plot raw data and model prediction ###
plotQuartiles = function(df, mod, varname, direction){
  qvarname = paste0("q.",varname)
  summarydf = summarySEwithin(df, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load",
                betweenvars=qvarname,
                na.rm=TRUE)
p.raw = ggplot(summarydf, aes_string(x="Load",y="residPCA",
                                        color=qvarname,
                                        group=qvarname)) +
  geom_line(size=1) +
  geom_errorbar(width=.2,size=1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
  theme_bw(20) + ylab("Change in Pupil Diameter") +
  scale_color_brewer(name="Quartile", palette='RdBu', direction=-1) + 
          theme(plot.title = element_text(size=20),
                axis.title = element_text(size=18),
                axis.text.x = element_text(size=16),
                legend.background = element_rect(fill = "transparent"),
                legend.justification=c(1,0), legend.position=c(1,0), 
                legend.text.align=1,
                legend.title.align=0,
                legend.title = element_text(size=16),
                legend.text = element_text(size=16))

# Plot predicted values
intterm = paste("facLoad", varname, sep=":")

dfpred = sjp.int(mod, type="eff", int.term=intterm, 
               swap.pred=T, mdrt.values = "quart", prnt.plot=F)$data.list[[1]]
levels(dfpred$grp) = seq(length(levels(dfpred$grp)))
p.pred = ggplot(data=subset(dfpred, !grp==3), aes(x=x, y=y, color=grp, group=grp)) + 
          geom_line(size=1) +
          geom_errorbar(width=.2,size=1, aes(ymin=conf.low,ymax=conf.high)) +
          ylab(expression(paste("Predicted ", Delta, " Pupil Diameter"))) + xlab("Load") +
          scale_color_brewer(name="Quartile",palette='RdBu',direction=direction,labels=seq(4)) + 
          scale_x_continuous(breaks=c(3,6,9)) + theme_bw(16) +
          theme(plot.title = element_text(size=20),
                axis.title = element_text(size=18),
                axis.text.x = element_text(size=16),
                legend.background = element_rect(fill = "transparent"),
                legend.justification=c(1,0), legend.position=c(1,0), 
                legend.text.align=1,
                legend.title.align=0,
                legend.title = element_text(size=16),
                legend.text = element_text(size=16))

g = arrangeGrob(p.raw, p.pred, top=varname, ncol=2)
g
}
```

-------------------------------

# Mixed Effects Models: All levels of load

## Choice RT

Run model testing interaction of load with log mean choice RT.
```{r}

lme.facLoad.CHRTGMEANLOG.MCI = lmer(residPCA ~ facLoad*(CHRTGMEANLOG_V2_nasp + 
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + Device + acamedbin + 
                                    (1 | case/vetsaid), REML=F, data=pupilRT)
summary(lme.facLoad.CHRTGMEANLOG.MCI)
anova(lme.facLoad.CHRTGMEANLOG.MCI)
```

Plot change in pupil dilation by log mean choice RT quartile.
```{r}
CHRTMEANLOG.fig = plotQuartiles(pupilRT, lme.facLoad.CHRTGMEANLOG.MCI, "CHRTGMEANLOG_V2_nasp", -1)
plot(CHRTMEANLOG.fig)
# ggsave("/home/jelman/netshare/K/Projects/Pupil_ReactionTime/results/PupilDilation_CHRTGMEANLOG_V2_nasp.png", 
#        CHRTMEANLOG.fig, height=6, width=12, dpi=300)
```


Run model testing interaction of load with log std choice RT.
```{r}

lme.facLoad.CHRTGSTDLOG.MCI = lmer(residPCA ~ facLoad*(CHRTGSTDLOG_V2_nasp + 
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + Device + acamedbin + 
                                    (1 | case/vetsaid), REML=F, data=pupilRT)
summary(lme.facLoad.CHRTGSTDLOG.MCI)
anova(lme.facLoad.CHRTGSTDLOG.MCI)
```

Plot change in pupil dilation by log std choice RT quartile.
```{r}
CHRTSTDLOG.fig = plotQuartiles(pupilRT, lme.facLoad.CHRTGSTDLOG.MCI, "CHRTGSTDLOG_V2_nasp", -1)
plot(CHRTSTDLOG.fig)
# ggsave("/home/jelman/netshare/K/Projects/Pupil_ReactionTime/results/PupilDilation_CHRTGSTDLOG_V2_nasp.png", 
#        CHRTSTDLOG.fig, height=6, width=12, dpi=300)
```


Run model testing interaction of load with CV choice RT.
```{r}

lme.facLoad.CHRTGCV.MCI = lmer(residPCA ~ facLoad*(CHRTGCV_V2_nasp + 
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + Device + acamedbin + 
                                    (1 | case/vetsaid), REML=F, data=pupilRT)
summary(lme.facLoad.CHRTGCV.MCI)
anova(lme.facLoad.CHRTGCV.MCI)
```

Plot change in pupil dilation by CV choice RT quartile.
```{r}
CHRTGCV.fig = plotQuartiles(pupilRT, lme.facLoad.CHRTGCV.MCI, "CHRTGCV_V2_nasp", -1)
plot(CHRTGCV.fig)
# ggsave("/home/jelman/netshare/K/Projects/Pupil_ReactionTime/results/PupilDilation_CHRTGCV_V2_nasp.png", 
#        CHRTGCV.fig, height=6, width=12, dpi=300)
```

Run model testing interaction of load with residualized log std choice RT.
```{r}

lme.facLoad.residCHRTGSTDLOG.MCI = lmer(residPCA ~ facLoad*(residCHRTGSTDLOG_V2_nasp + 
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + Device + acamedbin + 
                                    (1 | case/vetsaid), REML=F, data=pupilRT)
summary(lme.facLoad.residCHRTGSTDLOG.MCI)
anova(lme.facLoad.residCHRTGSTDLOG.MCI)
```

Plot change in pupil dilation by residualized log std choice RT quartile.
```{r}
residCHRTSTDLOG.fig = plotQuartiles(pupilRT, lme.facLoad.residCHRTGSTDLOG.MCI, "residCHRTGSTDLOG_V2_nasp", -1)
plot(residCHRTSTDLOG.fig)
# ggsave("/home/jelman/netshare/K/Projects/Pupil_ReactionTime/results/PupilDilation_residCHRTGSTDLOG_V2_nasp.png", 
#        residCHRTSTDLOG.fig, height=6, width=12, dpi=300)
```


Run model testing interaction of load with log mean and std choice RT.
```{r}

lme.facLoad.CHRTGMEANLOG.CHRTSTDLOG.MCI = lmer(residPCA ~ facLoad*(CHRTGMEANLOG_V2_nasp + 
                                                        CHRTGSTDLOG_V2_nasp +
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + Device + acamedbin + 
                                    (1 | case/vetsaid), REML=F, data=pupilRT)
summary(lme.facLoad.CHRTGMEANLOG.CHRTSTDLOG.MCI)
anova(lme.facLoad.CHRTGMEANLOG.CHRTSTDLOG.MCI)
```


## Simple RT

Run model testing interaction of load with log mean simple RT.
```{r}

lme.facLoad.SRTGMEANLOG.MCI = lmer(residPCA ~ facLoad*(SRTGMEANLOG_V2_nasp + 
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + Device + acamedbin + 
                                    (1 | case/vetsaid), REML=F, data=pupilRT)
summary(lme.facLoad.SRTGMEANLOG.MCI)
anova(lme.facLoad.SRTGMEANLOG.MCI)
```

Plot change in pupil dilation by log mean simple RT quartile.
```{r}
SRTMEANLOG.fig = plotQuartiles(pupilRT, lme.facLoad.SRTGMEANLOG.MCI, "SRTGMEANLOG_V2_nasp", -1)
plot(SRTMEANLOG.fig)
# ggsave("/home/jelman/netshare/K/Projects/Pupil_ReactionTime/results/PupilDilation_SRTGMEANLOG_V2_nasp.png", 
#        SRTMEANLOG.fig, height=6, width=12, dpi=300)
```


Run model testing interaction of load with log std simple RT.
```{r}

lme.facLoad.SRTGSTDLOG.MCI = lmer(residPCA ~ facLoad*(SRTGSTDLOG_V2_nasp + 
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + Device + acamedbin + 
                                    (1 | case/vetsaid), REML=F, data=pupilRT)
summary(lme.facLoad.SRTGSTDLOG.MCI)
anova(lme.facLoad.SRTGSTDLOG.MCI)
```

Plot change in pupil dilation by log std simple RT quartile.
```{r}
SRTSTDLOG.fig = plotQuartiles(pupilRT, lme.facLoad.SRTGSTDLOG.MCI, "SRTGSTDLOG_V2_nasp", -1)
plot(SRTSTDLOG.fig)
# ggsave("/home/jelman/netshare/K/Projects/Pupil_ReactionTime/results/PupilDilation_SRTGSTDLOG_V2_nasp.png", 
#        SRTSTDLOG.fig, height=6, width=12, dpi=300)
```


Run model testing interaction of load with CV simple RT.
```{r}

lme.facLoad.SRTGCV.MCI = lmer(residPCA ~ facLoad*(SRTGCV_V2_nasp + 
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + Device + acamedbin + 
                                    (1 | case/vetsaid), REML=F, data=pupilRT)
summary(lme.facLoad.SRTGCV.MCI)
anova(lme.facLoad.SRTGCV.MCI)
```

Plot change in pupil dilation by CV simple RT quartile.
```{r}
SRTGCV.fig = plotQuartiles(pupilRT, lme.facLoad.SRTGCV.MCI, "SRTGCV_V2_nasp", -1)
plot(SRTGCV.fig)
# ggsave("/home/jelman/netshare/K/Projects/Pupil_ReactionTime/results/PupilDilation_SRTGCV_V2_nasp.png", 
#        SRTGCV.fig, height=6, width=12, dpi=300)
```

Run model testing interaction of load with residualized log std simple RT.
```{r}

lme.facLoad.residSRTGSTDLOG.MCI = lmer(residPCA ~ facLoad*(residSRTGSTDLOG_V2_nasp + 
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + Device + acamedbin + 
                                    (1 | case/vetsaid), REML=F, data=pupilRT)
summary(lme.facLoad.residSRTGSTDLOG.MCI)
anova(lme.facLoad.residSRTGSTDLOG.MCI)
```

Plot change in pupil dilation by residualized log std simple RT quartile.
```{r}
residSRTSTDLOG.fig = plotQuartiles(pupilRT, lme.facLoad.residSRTGSTDLOG.MCI, "residSRTGSTDLOG_V2_nasp", -1)
plot(residSRTSTDLOG.fig)
# ggsave("/home/jelman/netshare/K/Projects/Pupil_ReactionTime/results/PupilDilation_residSRTGSTDLOG_V2_nasp.png", 
#        residSRTSTDLOG.fig, height=6, width=12, dpi=300)
```


Run model testing interaction of load with log mean and std simple RT.
```{r}

lme.facLoad.SRTGMEANLOG.SRTSTDLOG.MCI = lmer(residPCA ~ facLoad*(SRTGMEANLOG_V2_nasp + 
                                                        SRTGSTDLOG_V2_nasp +
                                                        c.DSFMAX_V2_nasp +
                                                        rMCI_cons_4grp) + 
                                    apoe4 + c.age_v2 + site_v2rev + Device + acamedbin + 
                                    (1 | case/vetsaid), REML=F, data=pupilRT)
summary(lme.facLoad.SRTGMEANLOG.SRTSTDLOG.MCI)
anova(lme.facLoad.SRTGMEANLOG.SRTSTDLOG.MCI)
```


# Mixed Effects Models: Within level of load

Test for differences based on log mean choice RT within each level of Load
```{r}
lme.CHRTGMEANLOG.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ CHRTGMEANLOG_V2_nasp + c.DSFMAX_V2_nasp + apoe4 + 
           c.age_v2 + site_v2rev + Device + acamedbin + rMCI_cons_4grp + 
                    (1 | case), 
         data=filter(pupilRT, Load==x))
})
lapply(lme.CHRTGMEANLOG.loads.MCI, summary)
```

Test for differences based on log std choice RT within each level of Load
```{r}
lme.CHRTGSTDLOG.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ CHRTGSTDLOG_V2_nasp + c.DSFMAX_V2_nasp + apoe4 + 
           c.age_v2 + site_v2rev + Device + acamedbin + rMCI_cons_4grp + 
                    (1 | case), 
         data=filter(pupilRT, Load==x))
})
lapply(lme.CHRTGSTDLOG.loads.MCI, summary)
```

Test for differences based on CV choice RT within each level of Load
```{r}
lme.CHRTGCV.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ CHRTGCV_V2_nasp + c.DSFMAX_V2_nasp + apoe4 + 
           c.age_v2 + site_v2rev + Device + acamedbin + rMCI_cons_4grp + 
                    (1 | case), 
         data=filter(pupilRT, Load==x))
})
lapply(lme.CHRTGCV.loads.MCI, summary)
```


----------------------------
# Covariate Plots 

Plot pupil dilation by digit span max quantile
```{r, echo=FALSE}
summaryResidPCA.DSFMAX_v2 = summarySEwithin(pupilRT, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load",
                betweenvars="q.DSFMAX_V2_nasp",
                na.rm=TRUE)
  
pDSFMAX_v2raw = summaryResidPCA.DSFMAX_v2 %>%
      ggplot(., aes(x=Load,y=residPCA,
                    color=q.DSFMAX_V2_nasp,
                    group=q.DSFMAX_V2_nasp)) +
        theme_bw(16) +
        ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
        geom_line(size=1) +
        geom_errorbar(width=.2,size=1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
        theme_bw(20) + ylab("Change in Pupil Diameter") +
        scale_color_brewer(name="d' quartile",palette='RdBu') + 
        theme(plot.title = element_text(size=20),
              axis.title = element_text(size=18),
              axis.text.x = element_text(size=16),
              legend.background = element_rect(fill = "transparent"),
              legend.justification=c(1,0), legend.position=c(1,0), 
              legend.text.align=1,
              legend.title.align=0,
              legend.title = element_text(size=16),
              legend.text = element_text(size=16))

print(pDSFMAX_v2raw)
# ggsave("~/netshare/K/Projects/Pupil_ReactionTime/results/pupilRT_MaxDigitSpan.pdf", pDSFMAX_v2raw)
```

Plot pupil dilation by MCI status
```{r, echo=FALSE}
summaryResidPCA.MCI = summarySEwithin(pupilRT, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load",
                betweenvars="rMCI_cons_4grp",
                na.rm=TRUE)
  
p.MCIraw = summaryResidPCA.MCI %>%
          ggplot(., aes(x=Load,y=residPCA,
                        color=rMCI_cons_4grp,
                        group=rMCI_cons_4grp)) +
        theme_bw(16) +
        ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
        geom_line(size=1) +
        geom_errorbar(width=.2,size=1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
        theme_bw(20) + ylab("Change in Pupil Diameter") +
          scale_color_brewer(name="MCI Status",palette='Set1',
                             labels=c("CN","naSMCI","aSMCI","MMCI")) + 
        theme(plot.title = element_text(size=20),
              axis.title = element_text(size=18),
              axis.text.x = element_text(size=16),
              legend.background = element_rect(fill = "transparent"),
              legend.justification=c(1,0), legend.position=c(1,0), 
              legend.text.align=1,
              legend.title.align=0,
              legend.title = element_text(size=16),
              legend.text = element_text(size=16))

print(p.MCIraw)
# ggsave("~/netshare/K/Projects/Pupil_ReactionTime/results/pupilRT_MCI.pdf", p.MCIraw)
```
----------------------------

```{r, include=FALSE}
#Save out analysis dataset
write.csv(pupilRT,
          "~/netshare/K/Projects/Pupil_ReactionTime/data/pupilDS_RT_AnalysisDataset.csv",
          row.names=F)
```

```{r}
print(sessionInfo(), locale = FALSE)
```