---
title: "Pupillometry and Processing Speed"
author: "Jeremy Elman"
date: "`r Sys.Date()`"
output: html_document
---


Load libraries
```{r results='hide', message=FALSE, warning=FALSE}
library(ggplot2)
library(gridExtra)
library(gtools)
library(lme4)
library(arm)
library(lmerTest)
library(dplyr)
library(magrittr)
library(sjPlot)
library(sjmisc)
library(multcomp)
source("K:/code/summarySE.R")
source("K:/code/normDataWithin.R")
source("K:/code/summarySEwithin.R")
source("K:/code/get_legend.R")
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
sjp.setTheme(theme=theme_bw())
```

Load data.
```{r, include=F}
pupilProcSpeed = read.csv("K:/Projects/Pupil_ReactionTime/data/pupil_ProcSpeed.csv", 
                         stringsAsFactors = FALSE)
pupilProcSpeed = pupilProcSpeed[!is.na(pupilProcSpeed$PCA),]
pupilProcSpeed = subset(pupilProcSpeed, VETSAGRP=='V1V2')
str(pupilProcSpeed)
```

Recode two-level factors to 0/1. Center continuous data.
*TRANSFORM*
```{r}
# Create factors
pupilProcSpeed$facLoad = factor(pupilProcSpeed$Load)
pupilProcSpeed$facLoad = relevel(pupilProcSpeed$facLoad, ref="6")
pupilProcSpeed$MZ = ifelse(pupilProcSpeed$zygos==1, 1, 0)
pupilProcSpeed$site_v2rev = ifelse(pupilProcSpeed$site_v2rev==1, 1, 0)
pupilProcSpeed$Device = factor(pupilProcSpeed$LR_Device)
pupilProcSpeed$acamedbin = ifelse(pupilProcSpeed$acamedtot==0, 0, 1)

#Bin MCI data into 0 = No impairment, 1 = Single domain MCI, 2 = Multi-domain MCI.
pupilProcSpeed$rMCI_cons_bin = ifelse(pupilProcSpeed$rMCI_cons_v2==0, 0, 
                                        ifelse(pupilProcSpeed$rMCI_cons_v2==1 | 
                                               pupilProcSpeed$rMCI_cons_v2==2, 1, 2))
pupilProcSpeed$rMCI_cons_bin = factor(pupilProcSpeed$rMCI_cons_bin)
pupilProcSpeed$rMCI_cons_v2 = factor(pupilProcSpeed$rMCI_cons_v2)

# Center continuous variables to interpret intercept at mean value (rather than 0).
# Subject specific variables centered at subject level, trial specific variables centered at trial level.
contTrialVars = c("PCA","pctPCA","adjPCA")
contSubjVars = c("age_v2","nas201tran","DSFMAX_v2")

# Center trial specific variables
for (x in contTrialVars) {
  newcol = paste0('c.',x)
  pupilProcSpeed[[newcol]] = as.numeric(scale(pupilProcSpeed[[x]], center=TRUE, scale=FALSE))
}

# Center subject specific variables
subjDF = pupilProcSpeed[c("vetsaid",contSubjVars)]
subjDF = subjDF %>% group_by(vetsaid) %>% dplyr::summarise_each(funs(first))
nums = sapply(subjDF, is.numeric)
c.subjDF = as.data.frame(apply(subjDF[,nums],2, function(y) y - mean(y, na.rm=TRUE)))
names(c.subjDF) = paste0("c.",names(c.subjDF))
c.subjDF$vetsaid = subjDF$vetsaid
pupilProcSpeed = left_join(pupilProcSpeed, c.subjDF, by="vetsaid")

# Plot centered data
hist(c.subjDF[!names(c.subjDF) %in% c("vetsaid")], main="Histograms of subject data")

# Create vectors of processing speed variables
psVars = c("strwraw","strcraw","TRL2TRAN","TRL3TRAN",
           "zstrwraw","zstrcraw","ztrl2tran","ztrl3tran","zProcSpeed")
psVarsV1 = paste0(psVars, "_v1")
psVarsV2 = paste0(psVars, "_v2")
psVarsV1V2 = c(psVarsV1, psVarsV2)

# Create measures of processing speed change. (V1 - V2 scores)
for (variable in psVars){
  varDiff = paste0("diff.",variable)
  varV1 = paste0(variable,"_v1")
  varV2 = paste0(variable,"_v2")
  pupilProcSpeed[[varDiff]] = pupilProcSpeed[[varV1]] - pupilProcSpeed[[varV2]]
}
diffVars = paste0("diff.",psVars)

# Create quantile groups
qVars = c("c.DSFMAX_v2",psVarsV1V2,diffVars)
new.qVars = qVars
names(new.qVars) = paste0("q.",qVars)
pupilProcSpeed = pupilProcSpeed %>%
  group_by(vetsaid) %>%
  dplyr::summarise_each_(funs(first),qVars) %>%
  mutate_each_(funs(quantcut(.,q=4, labels=seq(1,4))),qVars) %>%
  dplyr::select_("vetsaid"="vetsaid",.dots=new.qVars) %>%
  inner_join(pupilProcSpeed, by="vetsaid")

# Create residPCA by regressing BaselineDiameter from PCA and taking the residuals.
lme.PCA.resid = lmer(PCA ~ BaselineDiameter + (1 | case/vetsaid),
                     data=pupilProcSpeed)
pupilProcSpeed$residPCA = resid(lme.PCA.resid)
```

# Basic sample descriptives
```{r, include=FALSE}
#Create dataset with subject level variables to assess relationships with BOLD variance.

subjDatProcSpeed = pupilProcSpeed %>% 
            dplyr::select(-contains("PCA"),-contains("Load")) %>%
            group_by(vetsaid) %>%
            summarise_each(funs(first))
#write.csv(subjDatProcSpeed, "K:/Projects/Pupil_ReactionTime/data/ChoiceRT_subjDat.csv")
```

How many subjects?
```{r}
n_distinct(subjDatProcSpeed$vetsaid)
```

How many twin pairs vs unpaired twins? 
```{r}
subjDatProcSpeed %>%
  group_by(case) %>%
  dplyr::summarise(n_twins = n_distinct(vetsaid)) %>%
  dplyr::count(n_twins)
```


How many MZ and DZ pairs? (excludes unpaired subjects)
```{r}
subjDatProcSpeed %>% 
  group_by(case) %>%
  mutate(n_twins = n_distinct(vetsaid)) %>%
  filter(n_twins > 1) %>%
  dplyr::summarise(zyg = mean(zygos)) %>%
  group_by(zyg) %>%
  dplyr::count(zyg)
```

How many levels of load did subjects complete? Shows number of subjects who completed 1, 2, or 3 levels (corresponding to digit spans of 3, 6, and 9).
```{r}
pupilProcSpeed %>%
  group_by(vetsaid) %>%
  dplyr::summarise(load = n()) %>%
  dplyr::count(load)
```

How many of each MCI group?
```{r}
dplyr::count(subjDatProcSpeed, rMCI_cons_v2)
```

How many of each MCI group binned by single or multi-doman MCI?
```{r}
dplyr::count(subjDatProcSpeed, rMCI_cons_bin)
```

Look at frequencies of MCI measures
```{r}
mci.p1 = sjp.frq(subjDatProcSpeed$rMCI_cons_v2, 
          title="MCI groups",
          axisLabels.x=c("Normal","Single Domain\nNon-amnestic",
                         "Single Domain\nAmnestic","Multi Domain\nNon-Amnestic",
                         "Multi Domain Amnestic"),
          axisLimits.y = c(0,1000))

mci.p2 = sjp.frq(subjDatProcSpeed$rMCI_cons_bin, 
          title="Binned MCI groups",
          axisLabels.x=c("Normal","Single Domain MCI","Multi Domain MCI"),
          axisLimits.y = c(0,1000))

grid.arrange(mci.p1$plot,mci.p2$plot)
```

```{r, include=FALSE}
pdf("K:/Projects/Pupil_ReactionTime/results/procSpeed_MCI_groups.pdf", width=8, height=6)
grid.arrange(mci.p1$plot,mci.p2$plot)
dev.off()
```

Plot pctPCA and residPCA data to check for ceiling effects on pupil dilation
```{r}
pctPcaPlot = ggplot(pupilProcSpeed, aes(x=pctPCA)) + 
  geom_histogram(fill="steelblue3",color="black",size=.4) + 
  facet_wrap(~ Load, nrow=3) + 
  ggtitle("Histogram of pctPCA by Load") + 
  xlab("% PCA") + theme_bw() 

residPcaPlot = ggplot(pupilProcSpeed, aes(x=residPCA)) + 
  geom_histogram(fill="steelblue3",color="black",size=.4) + 
  facet_wrap(~ Load, nrow=3) + 
  ggtitle("Histogram of residPCA by Load") + 
  xlab("PCA (adjusted for baseline)") + theme_bw() 

grid.arrange(pctPcaPlot, residPcaPlot, ncol=2)
```


```{r, include=FALSE}
pdf("K:/Projects/Pupil_ReactionTime/results/procSpeed_PCAxLoad.pdf")
grid.arrange(pctPcaPlot, residPcaPlot, ncol=2)
dev.off()
```

Plot histograms of VETSA1 processing speed measures
```{r}
psSubsetV1 = subjDatProcSpeed %>% dplyr::select(one_of(psVarsV1))

plot_list = list()
for (i in 1:ncol(psSubsetV1)) {
  p = ggplot(psSubsetV1,aes_string(x = names(psSubsetV1)[i])) +
        geom_histogram(fill="steelblue3",color="black",size=.4) + 
        xlab(names(psSubsetV1[i])) + theme_bw()
  plot_list[[i]] = p
}


do.call(grid.arrange, c(plot_list, list(ncol=2)))
```

```{r, include=FALSE}
pdf("K:/Projects/Pupil_ReactionTime/results/procSpeed_psVarsV1_Hists.pdf")
do.call(grid.arrange, c(plot_list, list(ncol=2)))
dev.off()
```

Plot histograms of VETSA2 processing speed measures
```{r}
psSubsetV2 = subjDatProcSpeed %>% dplyr::select(one_of(psVarsV1))

plot_list = list()
for (i in 1:ncol(psSubsetV2)) {
  p = ggplot(psSubsetV2,aes_string(x = names(psSubsetV2)[i])) +
        geom_histogram(fill="steelblue3",color="black",size=.4) + 
        xlab(names(psSubsetV2[i])) + theme_bw()
  plot_list[[i]] = p
}


do.call(grid.arrange, c(plot_list, list(ncol=2)))
```

```{r, include=FALSE}
pdf("K:/Projects/Pupil_ReactionTime/results/procSpeed_psVarsV2_Hists.pdf")
do.call(grid.arrange, c(plot_list, list(ncol=2)))
dev.off()
```

Plot histograms of difference in processing speed measures between V1 & V2
```{r}
psSubsetV1V2diff = subjDatProcSpeed %>% dplyr::select(one_of(diffVars))

plot_list = list()
for (i in 1:ncol(psSubsetV1V2diff)) {
  p = ggplot(psSubsetV1V2diff,aes_string(x = names(psSubsetV1V2diff)[i])) +
        geom_histogram(fill="steelblue3",color="black",size=.4) + 
        xlab(names(psSubsetV1V2diff[i])) + theme_bw()
  plot_list[[i]] = p
}


do.call(grid.arrange, c(plot_list, list(ncol=2)))
```

```{r, include=FALSE}
pdf("K:/Projects/Pupil_ReactionTime/results/procSpeed_psVarsV1V2diff_Hists.pdf")
do.call(grid.arrange, c(plot_list, list(ncol=2)))
dev.off()
```

Plot pupil dilation of all VETSA 1 processing speed quantile groups
```{r}
measureListV1 = list()
for (measure in psVarsV1){
  measureListV1[[measure]] = summarySEwithin(pupilProcSpeed, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load", 
                betweenvars=paste0("q.",measure),
                na.rm=TRUE)
}

# Filter out NA cases (the above function doesn't always do this)
measureListV1 = lapply(measureListV1, function(df) df %>% filter(complete.cases(.)))

q.psVarsV1 = paste("q",psVarsV1, sep=".")
plot_listV1 = list()
for (i in 1:length(q.psVarsV1)) {
  p = ggplot(measureListV1[[i]], aes_string(x="Load",y="residPCA", 
                              color=q.psVarsV1[i], group=q.psVarsV1[i])) +
    geom_line() + 
    geom_errorbar(width=.1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
    ggtitle(paste0("Pupil dilation by ",q.psVarsV1[i]," quantile")) +
    theme_bw(14) + ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
    scale_color_discrete(name="quantile")
  plot_listV1[[i]] = p
}

# legend = get_legend(plot_list[[1]])
# for (i in 1:length(plot_list)) {
#   plot_list[[i]] = plot_list[[i]] + theme(legend.position="none")
# }
# plot_list$legend = legend

#Save out plot
pdf("K:/Projects/Pupil_ReactionTime/results/PCAxLoadxpsVarsV1_allGroups.pdf",width=15,height=12)
do.call(grid.arrange,  c(plot_listV1, list(ncol=3)))
dev.off()
```

Plot pupil dilation of all VETSA 2 processing speed quantile groups
```{r}
measureListV1V2diff = list()
for (measure in psVarsV2){
  measureListV1V2diff[[measure]] = summarySEwithin(pupilProcSpeed, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load", 
                betweenvars=paste0("q.",measure),
                na.rm=TRUE)
}

# Filter out NA cases (the above function doesn't always do this)
measureListV1V2diff = lapply(measureListV1V2diff, function(df) df %>% filter(complete.cases(.)))

q.psVarsV2 = paste("q",psVarsV2, sep=".")
plot_listV2 = list()
for (i in 1:length(q.psVarsV2)) {
  p = ggplot(measureListV1V2diff[[i]], aes_string(x="Load",y="residPCA", 
                              color=q.psVarsV2[i], group=q.psVarsV2[i])) +
    geom_line() + 
    geom_errorbar(width=.1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
    ggtitle(paste0("Pupil dilation by ",q.psVarsV2[i]," quantile")) +
    theme_bw(14) + ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
    scale_color_discrete(name="quantile")
  plot_listV2[[i]] = p
}

# legend = get_legend(plot_list[[1]])
# for (i in 1:length(plot_list)) {
#   plot_list[[i]] = plot_list[[i]] + theme(legend.position="none")
# }
# plot_list$legend = legend

#Save out plot
pdf("K:/Projects/Pupil_ReactionTime/results/PCAxLoadxpsVarsV2_allGroups.pdf",width=15,height=12)
do.call(grid.arrange,  c(plot_listV2, list(ncol=3)))
dev.off()
```

Plot pupil dilation of all processing speed change (v2 - V1) quantile groups
```{r}
measureListV1V2diff = list()
for (measure in diffVars){
  measureListV1V2diff[[measure]] = summarySEwithin(pupilProcSpeed, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load", 
                betweenvars=paste0("q.",measure),
                na.rm=TRUE)
}

# Filter out NA cases (the above function doesn't always do this)
measureListV1V2diff = lapply(measureListV1V2diff, function(df) df %>% filter(complete.cases(.)))

q.diffVars = paste("q",diffVars, sep=".")
plot_listV1V2diff = list()
for (i in 1:length(q.diffVars)) {
  p = ggplot(measureListV1V2diff[[i]], aes_string(x="Load",y="residPCA", 
                              color=q.diffVars[i], group=q.diffVars[i])) +
    geom_line() + 
    geom_errorbar(width=.1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
    ggtitle(paste0("Pupil dilation by ",q.diffVars[i]," quantile")) +
    theme_bw(14) + ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
    scale_color_discrete(name="quantile")
  plot_listV1V2diff[[i]] = p
}

# legend = get_legend(plot_list[[1]])
# for (i in 1:length(plot_list)) {
#   plot_list[[i]] = plot_list[[i]] + theme(legend.position="none")
# }
# plot_list$legend = legend

#Save out plot
pdf("K:/Projects/Pupil_ReactionTime/results/PCAxLoadxpsVarsV1V2diff_allGroups.pdf",
    width=15,height=12)
do.call(grid.arrange,  c(plot_listV1V2diff, list(ncol=3)))
dev.off()
```
-------------------------------
# Mixed Effects Models: Cognitively normal only

```{r, include=FALSE}
# Levels of load to test
loads = c(3,6,9)
```

**zProcSpeed_v2**
```{r, echo=FALSE}
plot_listV2[[9]]
```

Run basic model testing interaction of Load with VETSA 2 Processing Speed cognitive domain
```{r}
contrasts.facLoad.zProcSpeed_v2 = rbind(
    'Load3:zProcSpeed_v2 vs Load6:zProcSpeed_v2' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0),
    'Load6:zProcSpeed_v2 vs Load9:zProcSpeed_v2' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),
    'Load3:zProcSpeed_v2 vs Load9:zProcSpeed_v2' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0)
)
lme.facLoad.zProcSpeed_v2 = lmer(residPCA ~ facLoad*(zProcSpeed_v2 + c.DSFMAX_v2) + 
                                apoe4 + c.age_v2 + site_v2rev + Device + 
                                acamedbin + c.nas201tran + 
                                (1 | case/vetsaid),
                                data=subset(pupilProcSpeed,rMCI_cons_bin==0))
summary(lme.facLoad.zProcSpeed_v2)
summary(glht(lme.facLoad.zProcSpeed_v2, contrasts.facLoad.zProcSpeed_v2), 
              test = adjusted("none"))
```

Test for differences based on VETSA 1 Processing Speed cognitive domain within each level of Load
```{r}
lme.zProcSpeed_v2.loads <- lapply(loads, function(x) {
    lmer(residPCA ~ zProcSpeed_v2 + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + c.nas201tran + 
                    (1 | case), data=subset(pupilProcSpeed,Load==x &
                                              rMCI_cons_bin==0))
})
lapply(lme.zProcSpeed_v2.loads, summary)
```

**zProcSpeed_v1**
```{r, echo=FALSE}
plot_listV1[[9]]
```

Run basic model testing interaction of Load with VETSA 1 Processing Speed cognitive domain
```{r}
contrasts.facLoad.zProcSpeed_v1 = rbind(
    'Load3:zProcSpeed_v1 vs Load6:zProcSpeed_v1' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0),
    'Load6:zProcSpeed_v1 vs Load9:zProcSpeed_v1' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),
    'Load3:zProcSpeed_v1 vs Load9:zProcSpeed_v1' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0)
)
lme.facLoad.zProcSpeed_v1 = lmer(residPCA ~ facLoad*(zProcSpeed_v1 + c.DSFMAX_v2) + 
                                apoe4 + c.age_v2 + site_v2rev + Device + 
                                acamedbin + c.nas201tran + 
                                (1 | case/vetsaid),
                                data=subset(pupilProcSpeed,rMCI_cons_bin==0))
summary(lme.facLoad.zProcSpeed_v1)
summary(glht(lme.facLoad.zProcSpeed_v1, contrasts.facLoad.zProcSpeed_v1), 
              test = adjusted("none"))
```

Test for differences based on VETSA 1 Processing Speed cognitive domain within each level of Load
```{r}
lme.zProcSpeed_v1.loads <- lapply(loads, function(x) {
    lmer(residPCA ~ zProcSpeed_v1 + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + c.nas201tran + 
                    (1 | case), data=subset(pupilProcSpeed,Load==x &
                                              rMCI_cons_bin==0))
})
lapply(lme.zProcSpeed_v1.loads, summary)
```

Run basic model testing interaction of Load with VETSA 1 Processing Speed cognitive domain
```{r}
contrasts.facLoad.zProcSpeed_v1 = rbind(
    'Load3:zProcSpeed_v1 vs Load6:zProcSpeed_v1' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0),
    'Load6:zProcSpeed_v1 vs Load9:zProcSpeed_v1' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),
    'Load3:zProcSpeed_v1 vs Load9:zProcSpeed_v1' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0)
)
lme.facLoad.zProcSpeed_v1 = lmer(residPCA ~ facLoad*(zProcSpeed_v1 + c.DSFMAX_v2) + 
                                apoe4 + c.age_v2 + site_v2rev + Device + 
                                acamedbin + c.nas201tran + 
                                (1 | case/vetsaid),
                                data=subset(pupilProcSpeed,rMCI_cons_bin==0))
summary(lme.facLoad.zProcSpeed_v1)
summary(glht(lme.facLoad.zProcSpeed_v1, contrasts.facLoad.zProcSpeed_v1), 
              test = adjusted("none"))
```

Test for differences based on VETSA 1 Processing Speed cognitive domain within each level of Load
```{r}
lme.zProcSpeed_v1.loads <- lapply(loads, function(x) {
    lmer(residPCA ~ zProcSpeed_v1 + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + c.nas201tran + 
                    (1 | case), data=subset(pupilProcSpeed,Load==x &
                                              rMCI_cons_bin==0))
})
lapply(lme.zProcSpeed_v1.loads, summary)
```

**diff.zProcSpeed**
```{r, echo=FALSE}
plot_listV1V2diff[[9]]
```

Run basic model testing interaction of Load with difference between VETSA 1 & 2 Processing Speed cognitive domain
```{r}
contrasts.facLoad.diff.zProcSpeed = rbind(
    'Load3:diff.zProcSpeed vs Load6:diff.zProcSpeed' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0),
    'Load6:diff.zProcSpeed vs Load9:diff.zProcSpeed' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),
    'Load3:diff.zProcSpeed vs Load9:diff.zProcSpeed' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0)
)
lme.facLoad.diff.zProcSpeed = lmer(residPCA ~ facLoad*(diff.zProcSpeed + c.DSFMAX_v2) + 
                                apoe4 + c.age_v2 + site_v2rev + Device + 
                                acamedbin + c.nas201tran + 
                                (1 | case/vetsaid),
                                data=subset(pupilProcSpeed,rMCI_cons_bin==0))
summary(lme.facLoad.diff.zProcSpeed)
summary(glht(lme.facLoad.diff.zProcSpeed, contrasts.facLoad.diff.zProcSpeed), 
              test = adjusted("none"))
```

Test for differences based on difference between VETSA 1 & 2 Processing Speed cognitive domain within each level of Load
```{r}
lme.diff.zProcSpeed.loads <- lapply(loads, function(x) {
    lmer(residPCA ~ diff.zProcSpeed + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + c.nas201tran + 
                    (1 | case), data=subset(pupilProcSpeed,Load==x &
                                              rMCI_cons_bin==0))
})
lapply(lme.diff.zProcSpeed.loads, summary)
```
----------------
# Mixed Effects Models: All MCI groups

Run model (including MCI) testing interaction of Load with VETSA 2 Processing Speed cognitive domain
```{r}
contrasts.facLoad.zProcSpeed_v2.MCI = rbind(
    'Load3:zProcSpeed_v2 vs Load6:zProcSpeed_v2' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,0,0,0),
    'Load6:zProcSpeed_v2 vs Load9:zProcSpeed_v2' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
    'Load3:zProcSpeed_v2 vs Load9:zProcSpeed_v2' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0)
)

lme.facLoad.zProcSpeed_v2.MCI = lmer(residPCA ~ facLoad*(zProcSpeed_v2 + 
                                                        c.DSFMAX_v2 +
                                                        rMCI_cons_bin) + 
                                    apoe4 + c.age_v2 + site_v2rev + 
                                    Device + acamedbin + c.nas201tran + 
                                    (1 | case/vetsaid), data=pupilProcSpeed)
summary(lme.facLoad.zProcSpeed_v2.MCI)
summary(glht(lme.facLoad.zProcSpeed_v2.MCI, 
             contrasts.facLoad.zProcSpeed_v2.MCI),
             test = adjusted("none"))
```

Test for differences (including MCI) based on VETSA 2 Processing Speed cognitive domain within each level of Load
```{r}
lme.zProcSpeed_v2.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ zProcSpeed_v2 + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + 
                    rMCI_cons_bin + c.nas201tran + 
                    (1 | case), 
         data=filter(pupilProcSpeed, Load==x))
})
lapply(lme.zProcSpeed_v2.loads.MCI, summary)
```

Run  model (including MCI) testing interaction of Load with VETSA 1 Processing Speed cognitive domain
```{r}
contrasts.facLoad.zProcSpeed_v1.MCI = rbind(
    'Load3:zProcSpeed_v1 vs Load6:zProcSpeed_v1' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,0,0,0),
    'Load6:zProcSpeed_v1 vs Load9:zProcSpeed_v1' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
    'Load3:zProcSpeed_v1 vs Load9:zProcSpeed_v1' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0)
)

lme.facLoad.zProcSpeed_v1.MCI = lmer(residPCA ~ facLoad*(zProcSpeed_v1 + 
                                                        c.DSFMAX_v2 +
                                                        rMCI_cons_bin) + 
                                    apoe4 + c.age_v2 + site_v2rev + 
                                    Device + acamedbin + c.nas201tran + 
                                    (1 | case/vetsaid), data=pupilProcSpeed)
summary(lme.facLoad.zProcSpeed_v1.MCI)
summary(glht(lme.facLoad.zProcSpeed_v1.MCI, 
             contrasts.facLoad.zProcSpeed_v1.MCI),
             test = adjusted("none"))
```

Test for differences (including MCI) based on VETSA 1 Processing Speed cognitive domain within each level of Load
```{r}
lme.zProcSpeed_v1.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ zProcSpeed_v1 + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + 
                    rMCI_cons_bin + c.nas201tran + 
                    (1 | case), 
         data=filter(pupilProcSpeed, Load==x))
})
lapply(lme.zProcSpeed_v1.loads.MCI, summary)
```

Run  model (including MCI) testing interaction of Load with difference between VETSA 1 & 2 Processing Speed cognitive domain
```{r}
contrasts.facLoad.diff.zProcSpeed.MCI = rbind(
    'Load3:diff.zProcSpeed vs Load6:diff.zProcSpeed' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,0,0,0),
    'Load6:diff.zProcSpeed vs Load9:diff.zProcSpeed' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
    'Load3:diff.zProcSpeed vs Load9:diff.zProcSpeed' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0)
)

lme.facLoad.diff.zProcSpeed.MCI = lmer(residPCA ~ facLoad*(diff.zProcSpeed + 
                                                        c.DSFMAX_v2 +
                                                        rMCI_cons_bin) + 
                                    apoe4 + c.age_v2 + site_v2rev + 
                                    Device + acamedbin + c.nas201tran + 
                                    (1 | case/vetsaid), data=pupilProcSpeed)
summary(lme.facLoad.diff.zProcSpeed.MCI)
summary(glht(lme.facLoad.diff.zProcSpeed.MCI, 
             contrasts.facLoad.diff.zProcSpeed.MCI),
             test = adjusted("none"))
```

Test for differences (including MCI) based on difference between VETSA 1 & 2 Processing Speed cognitive domain within each level of Load
```{r}
lme.diff.zProcSpeed.loads.MCI <- lapply(loads, function(x) {
    lmer(residPCA ~ diff.zProcSpeed + apoe4 + c.age_v2 + site_v2rev + 
                    Device + acamedbin + c.DSFMAX_v2 + 
                    rMCI_cons_bin + c.nas201tran + 
                    (1 | case), 
         data=filter(pupilProcSpeed, Load==x))
})
lapply(lme.diff.zProcSpeed.loads.MCI, summary)
```

----------------------------
# Covariate Plots 

Plot pupil dilation by digit span max quantile
```{r, echo=FALSE}
summaryResidPCA.DSFMAX_v2 = summarySEwithin(pupilProcSpeed, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load",
                betweenvars="q.c.DSFMAX_v2",
                na.rm=TRUE)
# Filter out NA cases (the above function doesn't always do this)
summaryResidPCA.DSFMAX_v2 = summaryResidPCA.DSFMAX_v2 %>% filter(complete.cases(.))
  
p.DSFMAX_v2 = summaryResidPCA.DSFMAX_v2 %>%
          filter(q.c.DSFMAX_v2==1 | q.c.DSFMAX_v2==4) %>%
          ggplot(., aes(x=Load,y=residPCA,
                        color=q.c.DSFMAX_v2,
                        group=q.c.DSFMAX_v2)) +
            geom_line() +
            geom_errorbar(width=.1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
            ggtitle("Max digit span") + theme_bw(16) +
            ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
            scale_color_discrete(name="Max digit span\nquantile",
                                 labels=c("Lower","Upper"))
print(p.DSFMAX_v2)
ggsave("K:/Projects/Pupil_ReactionTime/results/pupilPS_MaxDigitSpan.pdf", p.DSFMAX_v2)
```

Plot pupil dilation by digit span max quantile
```{r, echo=FALSE}
summaryResidPCA.MCI = summarySEwithin(pupilProcSpeed, 
                measurevar="residPCA", 
                idvar="vetsaid", 
                withinvars="Load",
                betweenvars="rMCI_cons_bin",
                na.rm=TRUE)
# Filter out NA cases (the above function doesn't always do this)
summaryResidPCA.MCI = summaryResidPCA.MCI %>% filter(complete.cases(.))

p.MCI = summaryResidPCA.MCI %>%
          ggplot(., aes(x=Load,y=residPCA,
                        color=rMCI_cons_bin,
                        group=rMCI_cons_bin)) +
            geom_line() +
            geom_errorbar(width=.1, aes(ymin=residPCA-ci,ymax=residPCA+ci)) +
            ggtitle("MCI Status") + theme_bw(16) +
            ylab("Change in Pupil Diameter\n(Adjusted for Baseline)") +
            scale_color_discrete(name="MCI Group", 
                                 labels=c("No MCI",
                                          "Single Domain MCI",
                                          "Multi-Domain MCI"))
print(p.MCI)
ggsave("K:/Projects/Pupil_ReactionTime/results/pupilPS_MCI.pdf", p.MCI)
```
----------------------------

```{r, include=FALSE}
#Save out analysis dataset
write.csv(pupilProcSpeed,
          "K:/Projects/Pupil_ReactionTime/data/pupilDS_ChoiceRT_AnalysisDataset.csv",
          row.names=F)
```

```{r}
print(sessionInfo(), locale = FALSE)
```